---
title: 'Sensitivity Analysis: Flood Factor Groupings'
author: "Alvin Sheng"
output: 
  pdf_document:
    toc: true
---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(coda)
library(CARBayes)
library(ggplot2)
library(tidyverse)
```

```{r}
fhs_model_df <- readRDS(here("intermediary_data/sensitivity_analysis/fhs_model_df_ff_grouped.rds"))

var_names <- c("Intercept", "flood_ff_group1", "flood_ff_group2", "flood_ff_group3", 
               "EP_UNINSUR", "pollute_conc_pc1", "pollute_conc_pc2",
               "pollute_conc_pc3", "tmmx", "rmax", "Data_Value_CSMOKING")
```

```{r}
names_ff_grouped_strat <- c(paste("strat0", var_names, sep = ":"), 
                          paste("strat1", var_names, sep = ":"))
```



## Helper Functions

Function for post-processing the inference

```{r}
# extract the flood risk PC coefficients
# pc_idx is the vector of indices of the flood risk PC coefficients, after splitting data frame by strata
beta_data_frames_extract <- function(beta_inference_df, pc_idx) {
  
  beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]
  
  beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
  
  beta_pcs_strat0 <- beta_inference_df_strat0[pc_idx, ]
  
  beta_pcs_strat1 <- beta_inference_df_strat1[pc_idx, ]
  
  
  
  beta_pcs_strat0 <- mutate(beta_pcs_strat0, var_idx = factor(1:nrow(beta_pcs_strat0)))
  beta_pcs_strat1 <- mutate(beta_pcs_strat1, var_idx = factor(1:nrow(beta_pcs_strat1)))
  
  return(list(beta_pcs_strat0 = beta_pcs_strat0, beta_pcs_strat1 = beta_pcs_strat1))
  
}
```



# CAR model results, Coronary Heart Disease Stratified on RPL_THEMES

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/sensitivity_analysis/ff_grouped/all_census_tract_CHD.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- names_ff_grouped_strat
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/sensitivity_analysis/ff_grouped/beta_inference_files/CHD_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(3.5, 4.5, 7.5, 9.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 2, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, CHD, Stratified on All RPL Themes, Flood Factor Groupings") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/CHD_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:4
  
beta_CHD_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_CHD_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.04, 0.13)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3"), 6) + ggtitle("95% Credible Intervals for Flood Risk Groupings, Coronary Heart Disease") + 
  geom_point(data = beta_CHD_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_CHD_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/CHD_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```



# CAR model results, High Blood Pressure Stratified on RPL_THEMES

```{r}
load(here("modeling_files/sensitivity_analysis/ff_grouped/all_census_tract_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- names_ff_grouped_strat
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/sensitivity_analysis/ff_grouped/beta_inference_files/BPHIGH_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(3.5, 4.5, 7.5, 9.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 2, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, BPHIGH, Stratified on All RPL Themes, Flood Factor Groupings") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/BPHIGH_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:4
  
beta_BPHIGH_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_BPHIGH_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.23, 0.28)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3"), 6) + ggtitle("95% Credible Intervals for Flood Risk Groupings, High Blood Pressure") + 
  geom_point(data = beta_BPHIGH_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_BPHIGH_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/BPHIGH_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```



# CAR model results, Asthma Stratified on RPL_THEMES

```{r}
load(here("modeling_files/sensitivity_analysis/ff_grouped/all_census_tract_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- names_ff_grouped_strat
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/sensitivity_analysis/ff_grouped/beta_inference_files/CASTHMA_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(3.5, 4.5, 7.5, 9.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 2, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, CASTHMA, Stratified on All RPL Themes, Flood Factor Groupings") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/CASTHMA_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:4
  
beta_CASTHMA_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_CASTHMA_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.035, 0.0285)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3"), 6) + ggtitle("95% Credible Intervals for Flood Risk Groupings, Asthma") + 
  geom_point(data = beta_CASTHMA_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_CASTHMA_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/CASTHMA_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```





# CAR model results, Poor Mental Health Stratified on RPL_THEMES

```{r}
load(here("modeling_files/sensitivity_analysis/ff_grouped/all_census_tract_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- names_ff_grouped_strat
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/sensitivity_analysis/ff_grouped/beta_inference_files/MHLTH_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(3.5, 4.5, 7.5, 9.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 2, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, CASTHMA, Stratified on All RPL Themes, Flood Factor Groupings") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/MHLTH_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:4
  
beta_MHLTH_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_MHLTH_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.05, 0.055)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("FF Group 1", "FF Group 2", "FF Group 3"), 6) + ggtitle("95% Credible Intervals for Flood Risk Groupings, Poor Mental Health") + 
  geom_point(data = beta_MHLTH_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_MHLTH_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/ff_grouped/MHLTH_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```


