---
title: 'Sensitivity Analysis: Non-Spatial Models'
author: "Alvin Sheng"
output: 
  pdf_document:
    toc: true
---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Modeling Set-up

```{r}
library(here)
library(coda)
library(ggplot2)
library(tidyverse)
library(spdep)
```

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_fr_and_pollute_pc.rds"))

var_names <- c("Intercept", "flood_risk_pc1", "flood_risk_pc2",
               "flood_risk_pc3", "flood_risk_pc4", "flood_risk_pc5", 
               "EP_UNINSUR", "pollute_conc_pc1", "pollute_conc_pc2",
               "pollute_conc_pc3", "tmmx", "rmax", "Data_Value_CSMOKING")
```

Reading in adjacency matrix

```{r}
W <- readRDS(file = here("intermediary_data", "census_tract_adj_reorganize_all_census_tract.rds"))

# converting it to a form mat2listw() can understand
W <- as(W, "dMatrix")

# converting it to a form to be used in moran.test()
W_listw <- mat2listw(W)
```


```{r}
names_non_spat_strat <- c(paste("strat0", var_names, sep = ":"), 
                          paste("strat1", var_names, sep = ":"))
```

```{r}
# extract the four response variables
responses <- fhs_model_df[, (ncol(fhs_model_df) - 3):ncol(fhs_model_df)]
# extract the other covariates, except the SVI variables
covariates <- select(fhs_model_df[, -((ncol(fhs_model_df) - 3):ncol(fhs_model_df))], -EP_POV,
                     -EP_UNEMP, -EP_PCI, -EP_NOHSDP, 
                       -EP_AGE65, -EP_AGE17, -EP_DISABL, -EP_SNGPNT, 
                       -EP_MINRTY, -EP_LIMENG,
                       -EP_MUNIT, -EP_MOBILE, -EP_CROWD, -EP_NOVEH, -EP_GROUPQ)

first_var <- which(names(covariates) == "flood_risk_pc1")

strat_covariate <- fhs_model_df$RPL_THEMES
```

```{r}
# CHD
covariates_CHD <- data.frame(covariates, Data_Value_CHD = responses$Data_Value_CHD)
# BPHIGH
covariates_BPHIGH <- data.frame(covariates, Data_Value_BPHIGH = responses$Data_Value_BPHIGH)
# CASTHMA
covariates_CASTHMA <- data.frame(covariates, Data_Value_CASTHMA = responses$Data_Value_CASTHMA)
# MHLTH
covariates_MHLTH <- data.frame(covariates, Data_Value_MHLTH = responses$Data_Value_MHLTH)
```



## Helper Functions

Function to run the stratified non-spatial model

```{r}
source(here("scripts/sensitivity_analysis/non_spatial_strat_model.R"))
```

Function for post-processing the inference

```{r}
pc2flip <- c(-1, 1, -1, -1, -1, 
             -1, 1, -1, -1, -1)

post_flip <- function(beta_inf_subset, pc2flip) {
  names_temp <- colnames(beta_inf_subset)
  beta_inf_subset[pc2flip == -1, ] <- beta_inf_subset[pc2flip == -1, c(1, 3, 2)]
  colnames(beta_inf_subset) <- names_temp
  return(sweep(beta_inf_subset, 1, pc2flip, FUN = "*"))
}
```

```{r}
# extract the flood risk PC coefficients
# pc_idx is the vector of indices of the flood risk PC coefficients, after splitting data frame by strata
beta_data_frames_extract <- function(beta_inference_df, pc_idx) {
  
  beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]
  
  beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
  
  beta_pcs_strat0 <- beta_inference_df_strat0[pc_idx, ]
  
  beta_pcs_strat1 <- beta_inference_df_strat1[pc_idx, ]
  
  
  
  beta_pcs_strat0 <- mutate(beta_pcs_strat0, var_idx = factor(1:nrow(beta_pcs_strat0)))
  beta_pcs_strat1 <- mutate(beta_pcs_strat1, var_idx = factor(1:nrow(beta_pcs_strat1)))
  
  return(list(beta_pcs_strat0 = beta_pcs_strat0, beta_pcs_strat1 = beta_pcs_strat1))
  
}
```



# CAR model results, Coronary Heart Disease Stratified on RPL_THEMES

```{r}
chd_res <- non_spatial_strat_model(covariates_CHD, first_var, strat_covariate, strat_fn = median)

beta_results <- summary(chd_res$lm_obj)$coefficients
```

Moran's I test for spatial autocorrelation

```{r}
# mean imputing the residuals corresponding to missing Y values
resid_w_impute <- rep(NA, nrow(fhs_model_df))

resid_w_impute[!is.na(fhs_model_df$Data_Value_CHD)] <- chd_res$lm_obj$residuals

resid_w_impute[is.na(fhs_model_df$Data_Value_CHD)] <- 0
```

```{r}
(moran_results <- moran.test(resid_w_impute, W_listw))
```

The *p*-value is negligible, so we can reject the null hypothesis of zero spatial autocorrelation. Since the observed value of the Moran I statistic is significantly greater then the expected value, the residuals are positively autocorrelated, in contrast to negatively autocorrelated. Thus, using a CAR model is justified.

```{r}
row.names(beta_results) <- names_non_spat_strat
```

```{r}
beta_inference <- cbind(beta_results[, 1], 
                        beta_results[, 1] - 2 * beta_results[, 2], 
                        beta_results[, 1] + 2 * beta_results[, 2])
  
colnames(beta_inference) <- c("pt_est", "lb", "ub")

beta_inference <- round(beta_inference, 5)



pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = pt_est, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, CHD, Stratified on All RPL Themes, Non-Spatial") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/CHD_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:6
  
beta_CHD_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_CHD_pcs$beta_pcs_strat0, aes(x = var_idx, y = pt_est, color = strat)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6) + ggtitle("95% Credible Intervals for Flood Risk PCs, Coronary Heart Disease") + 
  geom_point(data = beta_CHD_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_CHD_pcs$beta_pcs_strat1, aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/CHD_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```



# CAR model results, High Blood Pressure Stratified on RPL_THEMES

```{r}
bphigh_res <- non_spatial_strat_model(covariates_BPHIGH, first_var, strat_covariate, strat_fn = median)

beta_results <- summary(bphigh_res$lm_obj)$coefficients
```

Moran's I test for spatial autocorrelation

```{r}
# mean imputing the residuals corresponding to missing Y values
resid_w_impute <- rep(NA, nrow(fhs_model_df))

resid_w_impute[!is.na(fhs_model_df$Data_Value_BPHIGH)] <- bphigh_res$lm_obj$residuals

resid_w_impute[is.na(fhs_model_df$Data_Value_BPHIGH)] <- 0
```

```{r}
(moran_results <- moran.test(resid_w_impute, W_listw))
```

The *p*-value is negligible, so we can reject the null hypothesis of zero spatial autocorrelation. Since the observed value of the Moran I statistic is significantly greater then the expected value, the residuals are positively autocorrelated, in contrast to negatively autocorrelated. Thus, using a CAR model is justified.

```{r}
row.names(beta_results) <- names_non_spat_strat
```

```{r}
beta_inference <- cbind(beta_results[, 1], 
                        beta_results[, 1] - 2 * beta_results[, 2], 
                        beta_results[, 1] + 2 * beta_results[, 2])
  
colnames(beta_inference) <- c("pt_est", "lb", "ub")

beta_inference <- round(beta_inference, 5)



pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = pt_est, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, BPHIGH, Stratified on All RPL Themes, Non-Spatial") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/BPHIGH_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:6
  
beta_BPHIGH_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_BPHIGH_pcs$beta_pcs_strat0, aes(x = var_idx, y = pt_est, color = strat)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6) + ggtitle("95% Credible Intervals for Flood Risk PCs, High Blood Pressure") + 
  geom_point(data = beta_BPHIGH_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_BPHIGH_pcs$beta_pcs_strat1, aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/BPHIGH_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```



# CAR model results, Asthma Stratified on RPL_THEMES

```{r}
casthma_res <- non_spatial_strat_model(covariates_CASTHMA, first_var, strat_covariate, strat_fn = median)

beta_results <- summary(casthma_res$lm_obj)$coefficients
```

Moran's I test for spatial autocorrelation

```{r}
# mean imputing the residuals corresponding to missing Y values
resid_w_impute <- rep(NA, nrow(fhs_model_df))

resid_w_impute[!is.na(fhs_model_df$Data_Value_CASTHMA)] <- casthma_res$lm_obj$residuals

resid_w_impute[is.na(fhs_model_df$Data_Value_CASTHMA)] <- 0
```

```{r}
(moran_results <- moran.test(resid_w_impute, W_listw))
```

The *p*-value is negligible, so we can reject the null hypothesis of zero spatial autocorrelation. Since the observed value of the Moran I statistic is significantly greater then the expected value, the residuals are positively autocorrelated, in contrast to negatively autocorrelated. Thus, using a CAR model is justified.

```{r}
row.names(beta_results) <- names_non_spat_strat
```

```{r}
beta_inference <- cbind(beta_results[, 1], 
                        beta_results[, 1] - 2 * beta_results[, 2], 
                        beta_results[, 1] + 2 * beta_results[, 2])
  
colnames(beta_inference) <- c("pt_est", "lb", "ub")

beta_inference <- round(beta_inference, 5)



pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = pt_est, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on All RPL Themes, Non-Spatial") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/CASTHMA_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:6
  
beta_CASTHMA_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_CASTHMA_pcs$beta_pcs_strat0, aes(x = var_idx, y = pt_est, color = strat)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6) + ggtitle("95% Credible Intervals for Flood Risk PCs, Asthma") + 
  geom_point(data = beta_CASTHMA_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_CASTHMA_pcs$beta_pcs_strat1, aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/CASTHMA_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```





# CAR model results, Poor Mental Health Stratified on RPL_THEMES

```{r}
mhlth_res <- non_spatial_strat_model(covariates_MHLTH, first_var, strat_covariate, strat_fn = median)

beta_results <- summary(mhlth_res$lm_obj)$coefficients
```

Moran's I test for spatial autocorrelation

```{r}
# mean imputing the residuals corresponding to missing Y values
resid_w_impute <- rep(NA, nrow(fhs_model_df))

resid_w_impute[!is.na(fhs_model_df$Data_Value_MHLTH)] <- mhlth_res$lm_obj$residuals

resid_w_impute[is.na(fhs_model_df$Data_Value_MHLTH)] <- 0
```

```{r}
(moran_results <- moran.test(resid_w_impute, W_listw))
```

The *p*-value is negligible, so we can reject the null hypothesis of zero spatial autocorrelation. Since the observed value of the Moran I statistic is significantly greater then the expected value, the residuals are positively autocorrelated, in contrast to negatively autocorrelated. Thus, using a CAR model is justified.

```{r}
row.names(beta_results) <- names_non_spat_strat
```

```{r}
beta_inference <- cbind(beta_results[, 1], 
                        beta_results[, 1] - 2 * beta_results[, 2], 
                        beta_results[, 1] + 2 * beta_results[, 2])
  
colnames(beta_inference) <- c("pt_est", "lb", "ub")

beta_inference <- round(beta_inference, 5)



pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



## Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                    rep("High SV", (nrow(beta_inference_df)/2))), levels = c("Low SV", "High SV"))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = pt_est, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, MHLTH, Stratified on All RPL Themes, Non-Spatial") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/MHLTH_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
pc_extract_idx <- 2:6
  
beta_MHLTH_pcs <- beta_data_frames_extract(beta_inference_df, pc_extract_idx)
```

```{r}
p <- ggplot(beta_MHLTH_pcs$beta_pcs_strat0, aes(x = var_idx, y = pt_est, color = strat)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = lb, ymax = ub, width = 0.4), col = "#F8766D") + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6) + ggtitle("95% Credible Intervals for Flood Risk PCs, Poor Mental Health") + 
  geom_point(data = beta_MHLTH_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_MHLTH_pcs$beta_pcs_strat1, aes(ymin = lb, ymax = ub, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/sensitivity_analysis/non_spatial/MHLTH_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```


