---
title: 'Sensitivity Analysis: Omitting Subsets of Variables'
author: "Alvin Sheng"
output: 
  pdf_document:
    toc: true
---

\newpage

```{r}
library(here)
library(coda)
library(CARBayes)
library(ggplot2)
library(tidyverse)
```

```{r}
fhs_model_df <- readRDS("intermediary_data/fhs_model_df_fr_and_pollute_pc.rds")

var_names <- c("Intercept", names(fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]))
```

```{r}
names_omit_svi <- var_names[!(var_names %in% c("EP_POV", "EP_UNEMP", "EP_PCI", "EP_NOHSDP", 
                                             "EP_AGE65", "EP_AGE17", "EP_DISABL", "EP_SNGPNT", 
                                             "EP_MINRTY", "EP_LIMENG", "EP_MUNIT", "EP_MOBILE", 
                                             "EP_CROWD", "EP_NOVEH", "EP_GROUPQ"))]
```

Function for post-processing the inference

```{r}
pc_idx <- 2:6
pc2flip <- c(-1, 1, -1, -1, -1)

post_flip <- function(beta_inf_subset, pc2flip) {
  names_temp <- colnames(beta_inf_subset)
  beta_inf_subset[pc2flip == -1, ] <- beta_inf_subset[pc2flip == -1, c(1, 3, 2)]
  colnames(beta_inf_subset) <- names_temp
  return(sweep(beta_inf_subset, 1, pc2flip, FUN = "*"))
}
```



# CHD Sensitivity Analysis

## CAR model results, Coronary Heart Disease, Omitting SVI

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/sensitivity_analysis/omit_subsets_of_variables/CHD_omit_SVI.RData"))
```

### Beta samples

```{r}
beta_samples <- mcmc.list(chain_list[[1]]$samples$beta, chain_list[[2]]$samples$beta, 
                          chain_list[[3]]$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F, include = F}
plot(beta_samples)
```

```{r, eval = F, include = F}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain_list[[1]]$samples$sigma2, chain_list[[2]]$samples$sigma2, 
                          chain_list[[3]]$samples$sigma2)

nu2_samples <- mcmc.list(chain_list[[1]]$samples$nu2, chain_list[[2]]$samples$nu2, 
                          chain_list[[3]]$samples$nu2)

```

```{r}
effectiveSize(sigma2_samples)
effectiveSize(nu2_samples)
```

```{r, eval = F, include = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r, eval = F, include = F}
gelman.diag(sigma2_samples)
```

```{r, eval = F, include = F}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain_list[[1]]$samples$phi, chain_list[[2]]$samples$phi, 
                          chain_list[[3]]$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r}
effectiveSize(phi_samples_subset)
```

```{r, eval = F, include = F}
plot(phi_samples_subset)
```

```{r, eval = F, include = F}
gelman.diag(phi_samples_subset)
```



### Inference

```{r}
beta_samples_matrix <- rbind(chain_list[[1]]$samples$beta, chain_list[[2]]$samples$beta, 
                          chain_list[[3]]$samples$beta)

colnames(beta_samples_matrix) <- names_omit_svi
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
# TODO
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_poverty.rds"))
```

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
# TODO
p <- ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  #geom_vline(xintercept = c(5.5, 21.5, 24.5, 26.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  #annotate(geom = "text", x = 3.5, y = 1.65, label = "Flood\nRisk",
           # col = "blue", size = 4.5) +
  #annotate(geom = "text", x = 13.5, y = 1.7, label = "Social Vulnerability Index",
           # col = "blue", size = 4.5) +
  # scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
  #                             "Poverty", "Unemployed", "Per Capita Income", "No High School",
  #                             "65 or Over", "17 or Under", "Disability",
  #                             "Single-Parent", "Minority", "Poor English",
  #                             "Multi-Unit", "Mobile", "Crowded",
  #                             "No Vehicle", "Group Quarters", "Uninsured",
  #                             "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
  #                             "Maximum Temperature", "Maximum Humidity",
  #                             "Smoking")) + 
  ggtitle("95% Credible Intervals of Coefficients, Coronary Heart Disease")

p
```

```{r}
# TODO
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_poverty.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



# BHIGH Sensitivity Analysis

## CAR model results, High Blood Pressure, Omitting SVI

```{r}
load(here("modeling_files/sensitivity_analysis/omit_subsets_of_variables/BPHIGH_omit_SVI.RData"))
```



### Inference

```{r}
beta_samples_matrix <- rbind(chain_list[[1]]$samples$beta, chain_list[[2]]$samples$beta, 
                          chain_list[[3]]$samples$beta)

colnames(beta_samples_matrix) <- names_omit_svi
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
# TODO
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_poverty.rds"))
```

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
# TODO
p <- ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  #geom_vline(xintercept = c(5.5, 21.5, 24.5, 26.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  #annotate(geom = "text", x = 3.5, y = 1.65, label = "Flood\nRisk",
           # col = "blue", size = 4.5) +
  #annotate(geom = "text", x = 13.5, y = 1.7, label = "Social Vulnerability Index",
           # col = "blue", size = 4.5) +
  # scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
  #                             "Poverty", "Unemployed", "Per Capita Income", "No High School",
  #                             "65 or Over", "17 or Under", "Disability",
  #                             "Single-Parent", "Minority", "Poor English",
  #                             "Multi-Unit", "Mobile", "Crowded",
  #                             "No Vehicle", "Group Quarters", "Uninsured",
  #                             "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
  #                             "Maximum Temperature", "Maximum Humidity",
  #                             "Smoking")) + 
  ggtitle("95% Credible Intervals of Coefficients, High Blood Pressure")

p
```

```{r}
# TODO
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_poverty.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```


