---
title: "Basic CAR Model"
author: "Alvin Sheng"
output: pdf_document
---

```{r}
library(here)
library(coda)
library(CARBayes)
library(ggplot2)
library(tidyverse)
```

```{r}
i_am("reports/basic_CAR_model_all_census_tract.Rmd")
```

```{r}
fhs_model_df <- readRDS("intermediary_data/fhs_model_df_all_census_tract_pc.rds")
```

# CAR model results

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by (), resulting in () samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/all_census_tract_intrinsic.RData"))
```



## Model Diagnostics

### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r, eval = F}
saveRDS(beta_samples, file = here("modeling_files/all_census_tract_intrinsic_beta_samples.rds"))
```

```{r, eval = F}
plot(beta_samples)
```

```{r}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r, eval = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r}
gelman.diag(sigma2_samples)
```

```{r}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r, eval = F}
plot(phi_samples_subset)
```

```{r}
gelman.diag(phi_samples_subset)
```



## Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))
```

```{r}
(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

Net Effect interpretation: what if each variable in a group (flood risk variables, SVIs, air pollution variables) increased by 1 standard deviation? What is the resulting change in the CHD prevalence?

<!-- ```{r} -->

<!-- sum(beta_inference[2:7, 1]) -->
<!-- sum(beta_inference[2:22, 1]) -->
<!-- sum(beta_inference[23:38, 1]) -->
<!-- sum(beta_inference[39:44, 1]) -->

<!-- ``` -->

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```

<!-- ## Presenting the Results -->

<!-- Retrieving the standard deviation used to scale the covariates -->

<!-- ```{r} -->
<!-- fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_sw_states_census_tract.rds")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- X <- fhs_model_df[, 14:(ncol(fhs_model_df) - 1)] -->

<!-- X <- X[, names(X) != "pct_floodfactor1"] -->

<!-- X <- as.matrix(X) -->



<!-- X           <- scale(X) # Scale covariates -->
<!-- # X[is.na(X)] <- 0        # Fill in missing values with the mean -->
<!-- ``` -->

<!-- ```{r} -->
<!-- (covariate_sds <- attr(X, "scaled:scale")) -->
<!-- ``` -->

<!-- Rescaling beta_inference (except the intercept) -->

<!-- ```{r} -->
<!-- beta_inference_scaled <- beta_inference -->

<!-- for (i in 2:nrow(beta_inference)) { -->

<!--   beta_inference_scaled[i, ] <- beta_inference_scaled[i, ] / covariate_sds[i - 1] -->

<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- beta_inference_scaled -->
<!-- ``` -->

<!-- Showing just the results for the significant coefficients -->

<!-- ```{r} -->
<!-- beta_inference_scaled[sign(beta_inference_scaled[, 2]) == sign(beta_inference_scaled[, 3]), ] -->
<!-- ``` -->

<!-- ```{r} -->
<!-- round(beta_inference_scaled[sign(beta_inference_scaled[, 2]) == sign(beta_inference_scaled[, 3]), ], digits = 3) -->
<!-- ``` -->

<!-- Multiplying by factor of 10, for more interpretability -->

<!-- ```{r} -->
<!-- round((beta_inference_scaled * 10)[sign(beta_inference_scaled[, 2]) == sign(beta_inference_scaled[, 3]), ], digits = 2) -->
<!-- ``` -->



<!-- ### Boxplots for the posterior distribution of coefficients -->

<!-- Scaling the posterior distributions of coefficients -->

<!-- ```{r} -->
<!-- beta_samples_scaled <- beta_samples_matrix -->

<!-- for (j in 2:ncol(beta_samples_matrix)) { -->

<!--   beta_samples_scaled[, j] <- beta_samples_scaled[, j] / covariate_sds[j - 1] -->

<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- beta_samples_scaled_10 <- beta_samples_scaled * 10 -->
<!-- ``` -->

<!-- ```{r} -->
<!-- round(t(apply(beta_samples_scaled_10, 2, quantile, c(0.5, 0.025, 0.975))),2) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- boxplot(beta_samples_scaled_10) -->
<!-- ``` -->



<!-- ```{r} -->
<!-- boxplot(beta_samples_scaled_10[, 2:13]) -->
<!-- boxplot(beta_samples_scaled_10[, 14:36]) -->


<!-- ``` -->

<!-- ```{r} -->
<!-- boxplot(beta_samples_matrix[, 2:13]) -->
<!-- abline(h = 0, col = "red") -->

<!-- boxplot(beta_samples_matrix[, 14:36]) -->
<!-- abline(h = 0, col = "Red") -->
<!-- ``` -->



<!-- ### Boxplots for the posterior distribution of coefficients, in ggplot -->

<!-- ```{r} -->
<!-- fl_coef_post <- stack(as.data.frame(beta_samples_matrix[, 2:13])) -->


<!-- ``` -->

<!-- ```{r} -->
<!-- ggplot(fl_coef_post) +  -->
<!--   geom_boxplot(aes(x = ind, y = values)) +  -->
<!--   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(),  -->
<!--        axis.text=element_text(size=12),  -->
<!--        plot.margin = margin(5.5, 5.5, 5.5, 20)) #+  -->
<!--   # geom_vline(xintercept = c(6.5, 12.5), col = "blue") +  -->
<!--   # geom_hline(yintercept = 0, col = "red") +  -->
<!--   # annotate(geom = "text", x = 3.5, y = 20, label = "Percentage of Properties\nat Risk",  -->
<!--   #          col = "blue", size = 4.5) +  -->
<!--   # annotate(geom = "text", x = 9.5, y = 20, label = "Average Risk Score\nof Properties",  -->
<!--   #          col = "blue", size = 4.5) +  -->
<!--   # annotate(geom = "text", x = 17, y = 20, label = "Percent of Properties with Risk Score",  -->
<!--   #          col = "blue", size = 4.5) + -->
<!--   # scale_x_discrete(labels = c("Certain, 2020", "Certain, 2050",  -->
<!--   #                             "Substantial, 2020", "Substantial, 2050", -->
<!--   #                             "Any, 2020", "Any, 2050", -->
<!--   #                             "All", "All except score 1",  -->
<!--   #                             "With Substantial Risk", "With Any Risk",  -->
<!--   #                             "In SFHA", "Not in SFHA",  -->
<!--   #                             "Score 2", "Score 3", "Score 4", "Score 5",  -->
<!--   #                             "Score 6", "Score 7", "Score 8", "Score 9",  -->
<!--   #                             "Score 10")) -->
<!-- ``` -->

<!-- Choropleth on the pct_floodfactor10 -->

<!-- ```{r} -->
<!-- other_coef_post <- stack(as.data.frame(beta_samples_matrix[, 14:36])) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ggplot(other_coef_post) +  -->
<!--   geom_boxplot(aes(x = ind, y = values)) +  -->
<!--   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(),  -->
<!--         axis.text=element_text(size=12),  -->
<!--         plot.margin = margin(5.5, 5.5, 5.5, 20)) #+ -->
<!--   # geom_vline(xintercept = c(16.5, 22.5), col = "blue") +  -->
<!--   # geom_hline(yintercept = 0, col = "red") + -->
<!--   # annotate(geom = "text", x = 8.5, y = 1.5, label = "Social Vulnerability Index",  -->
<!--   #          col = "blue", size = 4.5) +  -->
<!--   # annotate(geom = "text", x = 19.5, y = 1.5, label = "Air Pollution",  -->
<!--   #          col = "blue", size = 4.5) + -->
<!--   #   scale_x_discrete(labels = c("Poverty", "Unemployed", "Per Capita Income", "No High School",  -->
<!--   #                               "65 or Over", "17 or Under", "Disability",  -->
<!--   #                               "Single-Parent", "Minority", "Poor English",  -->
<!--   #                               "Multi-Unit", "Mobile", "Crowded",  -->
<!--   #                               "No Vehicle", "Group Quarters", "Uninsured",  -->
<!--   #                               "CO", "NO2", "O3", "PM10", "PM2.5", "SO2",  -->
<!--   #                               "Smoking")) -->

<!-- ``` -->



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 10)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(4.5, 20.5, 26.5, 30.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 2.5, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23.5, y = 1.5, label = "Air Pollution",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28.5, y = 1.5, label = "GRIDMET",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "CO", "NO2", "O3", "PM10", "PM2.5", "SO2",
                              "Summer Temperature", "Winter Temperature", "Summer Humidity", "Winter Humidity",
                              "Smoking"))
```


