---
title: "Basic CAR Model"
author: "Alvin Sheng"
date: "6/30/2021"
output: pdf_document
---

```{r}
library(here)
library(coda)
library(CARBayes)
```



# CAR model results

Inference is based on 3 markov chains, each of which has been run for 100000 samples, the first 10000 of which has been removed for burn-in. The remaining 90000 samples are thinned by 5, resulting in 18000 * 3 = 54000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/model_3chains_var_exclude.RData"))
```

Output for the first chain is shown below.

```{r}
chain1
```

The smallest effective sample size is 935.8, for ozone (o3). 

```{r}
chain1$accept
```

It appears that beta, phi, nu2, and tau2 probably have Gibbs steps, whereas rho has a Metropolis-Hastings step. In any case, the acceptance probabilities are acceptable. 



## Model Diagnostics

### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r, eval = F}
plot(beta_samples)
```

```{r}
gelman.diag(beta_samples)
```




### Examining tau2, nu2, rho

```{r}
tau2_samples <- mcmc.list(chain1$samples$tau2, chain2$samples$tau2, 
                          chain3$samples$tau2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                          chain3$samples$nu2)

rho_samples <- mcmc.list(chain1$samples$rho, chain2$samples$rho, 
                          chain3$samples$rho) 

```

```{r, eval = F}
plot(tau2_samples)

plot(nu2_samples)

plot(rho_samples)
```

```{r}
gelman.diag(tau2_samples)
```

```{r}
gelman.diag(nu2_samples)
```

```{r}
gelman.diag(rho_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:3108, size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r, eval = F}
plot(phi_samples_subset)
```

```{r}
gelman.diag(phi_samples_subset)
```



## Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- colnames(chain1$X)
```

```{r}
(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

List of significant beta coefficients:

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



