---
title: "Basic CAR Model"
author: "Alvin Sheng"
output: pdf_document
---

```{r}
library(here)
library(coda)
library(CARBayes)
library(ggplot2)
library(tidyverse)
```

```{r}
i_am("reports/basic_CAR_model_all_census_tract.Rmd")
```

```{r}
fhs_model_df <- readRDS("intermediary_data/fhs_model_df_fr_and_pollute_pc.rds")
```

Function for post-processing the inference

```{r}
pc_idx <- 2:6
pc2flip <- c(-1, 1, -1, -1, -1)

post_flip <- function(beta_inf_subset, pc2flip) {
  names_temp <- colnames(beta_inf_subset)
  beta_inf_subset[pc2flip == -1, ] <- beta_inf_subset[pc2flip == -1, c(1, 3, 2)]
  colnames(beta_inf_subset) <- names_temp
  return(sweep(beta_inf_subset, 1, pc2flip, FUN = "*"))
}
```




# CAR model results, Coronary Heart Disease

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/all_census_tract_intrinsic.RData"))
```

## Model Diagnostics

## Residual Plots

For each chain

```{r}
plot(chain1$mean.fitted, chain1$residuals$pearson)

abline(h = 0, col = "red")
```

```{r}
plot(chain2$mean.fitted, chain2$residuals$pearson)

abline(h = 0, col = "red")
```

```{r}
plot(chain3$mean.fitted, chain3$residuals$pearson)

abline(h = 0, col = "red")
```

```{r}
qqnorm(chain1$residuals$pearson)

qqline(chain1$residuals$pearson)
```

What's the proportion of predicted values that correspond to negative counts? Which would not make sense

```{r}
mean(chain1$mean.fitted < 0, na.rm = T)
```

Small proportion seems reasonable. 



### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F}
plot(beta_samples)
```

```{r}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r, eval = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r}
gelman.diag(sigma2_samples)
```

```{r}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r, eval = F}
plot(phi_samples_subset)
```

```{r}
gelman.diag(phi_samples_subset)
```



## Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]))
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

<!-- Net Effect interpretation: what if each variable in a group (flood risk variables, SVIs, air pollution variables) increased by 1 standard deviation? What is the resulting change in the dependent variable? -->

<!-- ```{r} -->

<!-- sum(beta_inference[2:7, 1]) -->
<!-- sum(beta_inference[2:22, 1]) -->
<!-- sum(beta_inference[23:38, 1]) -->
<!-- sum(beta_inference[39:44, 1]) -->

<!-- ``` -->

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
p <- ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(5.5, 21.5, 24.5, 26.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3.5, y = 1.65, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13.5, y = 1.7, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals of Coefficients, Coronary Heart Disease")

p
```

```{r}
ggsave(here("figures/final_figures/CHD_cred_intervals.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



```{r}
p <- ggplot(beta_inference_df[2:6, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5")) + ggtitle("95% Credible Intervals for Flood Risk PCs, Coronary Heart Disease")

p
```

```{r}
ggsave(here("figures/final_figures/CHD_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



# CAR model results, High Blood Pressure

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/all_census_tract_BPHIGH.RData"))
```

## Model Diagnostics

### Residual plot

```{r}
plot(chain1$mean.fitted, chain1$residuals$pearson)

abline(h = 0, col = "red")
```

```{r}
qqnorm(chain1$residuals$pearson)

qqline(chain1$residuals$pearson)
```



### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F}
plot(beta_samples)
```

```{r}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r, eval = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r}
gelman.diag(sigma2_samples)
```

```{r}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r, eval = F}
plot(phi_samples_subset)
```

```{r}
gelman.diag(phi_samples_subset)
```



## Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]))
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

<!-- Net Effect interpretation: what if each variable in a group (flood risk variables, SVIs, air pollution variables) increased by 1 standard deviation? What is the resulting change in the dependent variable? -->

<!-- ```{r} -->

<!-- sum(beta_inference[2:7, 1]) -->
<!-- sum(beta_inference[2:22, 1]) -->
<!-- sum(beta_inference[23:38, 1]) -->
<!-- sum(beta_inference[39:44, 1]) -->

<!-- ``` -->

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
p <- ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(5.5, 21.5, 24.5, 26.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3.5, y = 4.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13.5, y = 4.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals of Coefficients, High Blood Pressure")

p
```

```{r}
ggsave(here("figures/final_figures/BPHIGH_cred_intervals.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
p <- ggplot(beta_inference_df[2:6, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5")) + ggtitle("95% Credible Intervals for Flood Risk PCs, High Blood Pressure")

p
```

```{r}
ggsave(here("figures/final_figures/BPHIGH_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



# CAR model results, Asthma

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/all_census_tract_CASTHMA.RData"))
```

## Model Diagnostics

### Residual plot

```{r}
plot(chain1$mean.fitted, chain1$residuals$pearson)

abline(h = 0, col = "red")
```

```{r}
qqnorm(chain1$residuals$pearson)

qqline(chain1$residuals$pearson)
```



### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F}
plot(beta_samples)
```

```{r}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r, eval = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r}
gelman.diag(sigma2_samples)
```

```{r}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r, eval = F}
plot(phi_samples_subset)
```

```{r}
gelman.diag(phi_samples_subset)
```



## Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]))
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

<!-- Net Effect interpretation: what if each variable in a group (flood risk variables, SVIs, air pollution variables) increased by 1 standard deviation? What is the resulting change in the dependent variable? -->

<!-- ```{r} -->

<!-- sum(beta_inference[2:7, 1]) -->
<!-- sum(beta_inference[2:22, 1]) -->
<!-- sum(beta_inference[23:38, 1]) -->
<!-- sum(beta_inference[39:44, 1]) -->

<!-- ``` -->

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
p <- ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(5.5, 21.5, 24.5, 26.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3.5, y = 1.05, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13.5, y = 1.1, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals of Coefficients, Asthma")

p
```

```{r}
ggsave(here("figures/final_figures/CASTHMA_cred_intervals.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
p <- ggplot(beta_inference_df[2:6, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5")) + ggtitle("95% Credible Intervals for Flood Risk PCs, Asthma")

p
```

```{r}
ggsave(here("figures/final_figures/CASTHMA_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



# CAR model results, Poor Mental Health

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/all_census_tract_MHLTH.RData"))
```

## Model Diagnostics

### Residual plot

```{r}
plot(chain1$mean.fitted, chain1$residuals$pearson)

abline(h = 0, col = "red")
```

```{r}
qqnorm(chain1$residuals$pearson)

qqline(chain1$residuals$pearson)
```



### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F}
plot(beta_samples)
```

```{r}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r, eval = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r}
gelman.diag(sigma2_samples)
```

```{r}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r, eval = F}
plot(phi_samples_subset)
```

```{r}
gelman.diag(phi_samples_subset)
```



## Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]))
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

<!-- Net Effect interpretation: what if each variable in a group (flood risk variables, SVIs, air pollution variables) increased by 1 standard deviation? What is the resulting change in the dependent variable? -->

<!-- ```{r} -->

<!-- sum(beta_inference[2:7, 1]) -->
<!-- sum(beta_inference[2:22, 1]) -->
<!-- sum(beta_inference[23:38, 1]) -->
<!-- sum(beta_inference[39:44, 1]) -->

<!-- ``` -->

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

```{r}
p <- ggplot(beta_inference_df[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(5.5, 21.5, 24.5, 26.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3.5, y = 2.35, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13.5, y = 2.4, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals of Coefficients, Poor Mental Health")

p
```

```{r}
ggsave(here("figures/final_figures/MHLTH_cred_intervals.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

```{r}
p <- ggplot(beta_inference_df[2:6, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_hline(yintercept = 0, col = "red") +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5")) + ggtitle("95% Credible Intervals for Flood Risk PCs, Poor Mental Health")

p
```

```{r}
ggsave(here("figures/final_figures/MHLTH_cred_intervals_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```


