---
title: "Calculations for the Revisions"
author: "Alvin Sheng"
date: "2023-08-28"
output: pdf_document
---

```{r}
library(here)
library(readxl)
library(stringr)
library(tidyverse)
library(tidyr)
library(Matrix)

library(sf)

select <- dplyr::select
```

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_fr_and_pollute_pc.rds"))
```

# Double checking summary statistics of missingness across the responses and covariates

In particular, the median and maximum

```{r}
summary(apply(fhs_model_df[, 19:ncol(fhs_model_df)], 2, function(vec) {mean(is.na(vec))}))
```

# Checking distribution of the responses

```{r}
hist(fhs_model_df$Data_Value_CHD)
qqnorm(fhs_model_df$Data_Value_CHD)
qqline(fhs_model_df$Data_Value_CHD)
```

```{r}
hist(fhs_model_df$Data_Value_BPHIGH)
qqnorm(fhs_model_df$Data_Value_BPHIGH)
qqline(fhs_model_df$Data_Value_BPHIGH)
```

```{r}
hist(fhs_model_df$Data_Value_CASTHMA)
qqnorm(fhs_model_df$Data_Value_CASTHMA)
qqline(fhs_model_df$Data_Value_CASTHMA)
```

```{r}
hist(fhs_model_df$Data_Value_MHLTH)
qqnorm(fhs_model_df$Data_Value_MHLTH)
qqline(fhs_model_df$Data_Value_MHLTH)
```



# Variability of response variables among census tracts 

```{r}
# work with the PLACES dataset
# https://chronicdata.cdc.gov/500-Cities-Places/PLACES-Local-Data-for-Better-Health-Census-Tract-D/cwsq-ngmh 

places_dat <- read.csv(here("imported_data", 
                            "PLACES__Local_Data_for_Better_Health__Census_Tract_Data_2020_release.csv"))

# don't need the year, state_abbr, lat or lon

places_subset <- dplyr::select(places_dat, -c(Year, StateAbbr, StateDesc, LocationName, 
                                              DataSource, Category, Data_Value_Unit, Data_Value_Type, 
                                              Data_Value_Footnote_Symbol, Data_Value_Footnote, 
                                              Geolocation, DataValueTypeID))

# convert from long to wide format

places_dat_wide <- pivot_wider(places_subset, id_cols = c(LocationID, CountyFIPS, TotalPopulation),
                               names_from = MeasureId, 
                               values_from = c(Data_Value, Low_Confidence_Limit, High_Confidence_Limit))

places_dat_wide <- rename(places_dat_wide, fips = LocationID)
```

```{r}
# checking heteroskedasticity
summary(places_dat_wide$High_Confidence_Limit_CHD - places_dat_wide$Low_Confidence_Limit_CHD)
sd(places_dat_wide$Data_Value_CHD)

summary(places_dat_wide$High_Confidence_Limit_BPHIGH - places_dat_wide$Low_Confidence_Limit_BPHIGH)
sd(places_dat_wide$Data_Value_BPHIGH)

summary(places_dat_wide$High_Confidence_Limit_CASTHMA - places_dat_wide$Low_Confidence_Limit_CASTHMA)
sd(places_dat_wide$Data_Value_CASTHMA)

summary(places_dat_wide$High_Confidence_Limit_MHLTH - places_dat_wide$Low_Confidence_Limit_MHLTH)
sd(places_dat_wide$Data_Value_MHLTH)
```



# Checking Census Tract Statistics

```{r}
summary(fhs_model_df$E_TOTPOP)
summary(fhs_model_df$E_HU)
summary(fhs_model_df$E_HH)
```

```{r}
sd(fhs_model_df$E_TOTPOP, na.rm = T)
sd(fhs_model_df$E_HU, na.rm = T)
sd(fhs_model_df$E_HH, na.rm = T)
```

# Checking distributions of the stratification variables

```{r}
hist(fhs_model_df$EP_POV)
abline(v = median(fhs_model_df$EP_POV, na.rm = T), col = "red")

hist(fhs_model_df$RPL_THEME1)
abline(v = median(fhs_model_df$RPL_THEME1, na.rm = T), col = "red")

hist(fhs_model_df$RPL_THEME2)
abline(v = median(fhs_model_df$RPL_THEME2, na.rm = T), col = "red")

hist(fhs_model_df$RPL_THEME3)
abline(v = median(fhs_model_df$RPL_THEME3, na.rm = T), col = "red")

hist(fhs_model_df$RPL_THEME4)
abline(v = median(fhs_model_df$RPL_THEME4, na.rm = T), col = "red")

hist(fhs_model_df$RPL_THEMES)
abline(v = median(fhs_model_df$RPL_THEMES, na.rm = T), col = "red")
```

Doing single histogram with median line, for single SVIs

```{r, eval = F}
par(mfrow = c(5, 3))

hist(fhs_model_df$EP_POV, main = "% Below Poverty Level", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_POV, na.rm = T), col = "red")

hist(fhs_model_df$EP_UNEMP, main = "% Unemployed", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_UNEMP, na.rm = T), col = "red")

hist(fhs_model_df$EP_PCI, main = "Per Capita Income", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_PCI, na.rm = T), col = "red")

hist(fhs_model_df$EP_NOHSDP, main = "% No High School Diploma", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_NOHSDP, na.rm = T), col = "red")

hist(fhs_model_df$EP_AGE65, main = "% Over 65", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_AGE65, na.rm = T), col = "red")

hist(fhs_model_df$EP_AGE17, main = "% Under 17", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_AGE17, na.rm = T), col = "red")

hist(fhs_model_df$EP_DISABL, main = "% Disabled", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_DISABL, na.rm = T), col = "red")

hist(fhs_model_df$EP_SNGPNT, main = "% Households Single Parent", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_SNGPNT, na.rm = T), col = "red")

hist(fhs_model_df$EP_MINRTY, main = "% Minority", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_MINRTY, na.rm = T), col = "red")

hist(fhs_model_df$EP_LIMENG, main = "% Limited English", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_LIMENG, na.rm = T), col = "red")

hist(fhs_model_df$EP_MUNIT, main = "% Housing With More Than 10 Units", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_MUNIT, na.rm = T), col = "red")

hist(fhs_model_df$EP_MOBILE, main = "% Mobile Homes", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_MOBILE, na.rm = T), col = "red")

hist(fhs_model_df$EP_CROWD, main = "% Crowded Housing", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_CROWD, na.rm = T), col = "red")

hist(fhs_model_df$EP_NOVEH, main = "% Households Without Vehicles", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_NOVEH, na.rm = T), col = "red")

hist(fhs_model_df$EP_GROUPQ, main = "% Persons in Group Quarters", xlab = NULL, ylab= NULL)
abline(v = median(fhs_model_df$EP_GROUPQ, na.rm = T), col = "red")

# export as US Letter, Portrait, as figures/final_figures/SVI_distributions.pdf 
```

```{r}
strat_fn <- median

strat_covariate <- fhs_model_df$EP_POV
strat_covariate[is.na(strat_covariate)] <- mean(strat_covariate, na.rm = T)

strat <- ifelse(strat_covariate <= strat_fn(strat_covariate), "Below Median", "Above Median")
strat <- factor(strat, levels = c("Below Median", "Above Median"))

hist_dat <- data.frame(values = strat_covariate, strat = strat)

ggplot(hist_dat, aes(x = values, fill = strat)) +                       # Draw overlaying histogram
  geom_histogram(position = "identity", alpha = 0.7, bins = 50)
```



# Checking Linear Regression Assumptions for Models Stratified on all SVI Themes

```{r}
# loading requisite data

load(here("modeling_files/stratified_analysis/model_stratif_rpls.RData"))
CHD.mean.fitted <- (chain1$mean.fitted + chain2$mean.fitted + chain3$mean.fitted) / 3
CHD.mean.phi <- (chain1$samples$mean.phi + chain2$samples$mean.phi + chain3$samples$mean.phi) / 3
CHD.mean.resid <- (chain1$residuals$response + chain2$residuals$response + chain3$residuals$response) / 3
CHD.mean.beta <- apply(rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta), 2, mean)

load(here("modeling_files/stratified_analysis/model_stratif_rpls_BPHIGH.RData"))
BPHIGH.mean.fitted <- (chain1$mean.fitted + chain2$mean.fitted + chain3$mean.fitted) / 3
BPHIGH.mean.phi <- (chain1$samples$mean.phi + chain2$samples$mean.phi + chain3$samples$mean.phi) / 3
BPHIGH.mean.resid <- (chain1$residuals$response + chain2$residuals$response + chain3$residuals$response) / 3
BPHIGH.mean.beta <- apply(rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta), 2, mean)

load(here("modeling_files/stratified_analysis/model_stratif_rpls_CASTHMA.RData"))
CASTHMA.mean.fitted <- (chain1$mean.fitted + chain2$mean.fitted + chain3$mean.fitted) / 3
CASTHMA.mean.phi <- (chain1$samples$mean.phi + chain2$samples$mean.phi + chain3$samples$mean.phi) / 3
CASTHMA.mean.resid <- (chain1$residuals$response + chain2$residuals$response + chain3$residuals$response) / 3
CASTHMA.mean.beta <- apply(rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta), 2, mean)

load(here("modeling_files/stratified_analysis/model_stratif_rpls_MHLTH.RData"))
MHLTH.mean.fitted <- (chain1$mean.fitted + chain2$mean.fitted + chain3$mean.fitted) / 3
MHLTH.mean.phi <- (chain1$samples$mean.phi + chain2$samples$mean.phi + chain3$samples$mean.phi) / 3
MHLTH.mean.resid <- (chain1$residuals$response + chain2$residuals$response + chain3$residuals$response) / 3
MHLTH.mean.beta <- apply(rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta), 2, mean)
```

QQ-plots

```{r}
qqnorm(CHD.mean.resid)
qqline(CHD.mean.resid)

qqnorm(BPHIGH.mean.resid)
qqline(BPHIGH.mean.resid)

qqnorm(CASTHMA.mean.resid)
qqline(CASTHMA.mean.resid)

qqnorm(MHLTH.mean.resid)
qqline(MHLTH.mean.resid)
```

Residuals vs. Fitted

```{r}
plot(CHD.mean.fitted, CHD.mean.resid)
```

```{r}
plot(BPHIGH.mean.fitted, BPHIGH.mean.resid)
```

```{r}
plot(CASTHMA.mean.fitted, CASTHMA.mean.resid)
```

```{r}
plot(MHLTH.mean.fitted, MHLTH.mean.resid)
```


