---
title: "CAR model Divide and Conquer"
author: "Alvin Sheng"
date: "11/17/2021"
output: pdf_document
---

```{r}
library(here)
library(coda)

i_am("reports/CARmodel_div_and_conq.Rmd")
```

```{r}
fhs_model_df <- readRDS("intermediary_data/fhs_model_df_all_census_tract_pc.rds")
```



# Northeastern States

```{r}

load(here("modeling_files/census_tract_ne.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
effectiveSize(chain1$samples$phi)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_ne <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_ne, c(0.5, 0.025, 0.975))
```



# Mid-Atlantic States

```{r}

load(here("modeling_files/census_tract_at.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_at <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_at, c(0.5, 0.025, 0.975))
```



# Midwest States

```{r}

load(here("modeling_files/census_tract_mw.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_mw <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_mw, c(0.5, 0.025, 0.975))
```



# Southwest States

```{r}

load(here("modeling_files/census_tract_sw.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_sw <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_sw, c(0.5, 0.025, 0.975))
```





# Northwestern States

```{r}

load(here("modeling_files/census_tract_nw.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_nw <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_nw, c(0.5, 0.025, 0.975))
```





# Western States

```{r}

load(here("modeling_files/census_tract_we.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_we <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_we, c(0.5, 0.025, 0.975))
```



# Southeastern States

```{r}

load(here("modeling_files/census_tract_se.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)

effectiveSize(chain1$samples$rho)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

```{r}
rho_samples_se <- c(chain1$samples$rho, chain2$samples$rho, chain3$samples$rho)

quantile(rho_samples_se, c(0.5, 0.025, 0.975))
```

# Finding the average $\rho$

collect the rho_samples across all seven models, take grand average (sum, then divide by 60000 * 7).

Actually, consider weighting by number of census tracts in each region. So, first get individual average rho's. Then, weight according to number of census tracts in the region. 

```{r}
mean(rho_samples_ne)
mean(rho_samples_at)
mean(rho_samples_mw)
mean(rho_samples_sw)
mean(rho_samples_nw)
mean(rho_samples_we)
mean(rho_samples_se)
```

```{r}
(mean(rho_samples_ne) * 10321 + mean(rho_samples_at) * 11479 + mean(rho_samples_mw) * 10935 + 
   mean(rho_samples_sw) * 11321 + mean(rho_samples_nw) * 6885 + mean(rho_samples_we) * 8743 + 
   mean(rho_samples_se) * 12853) / (10321 + 11479 + 10935 + 11321 + 6885 + 8743 + 12853)
```

Weighted rho: 0.9918268. 


# Intrinsic CAR model

```{r}

load(here("modeling_files/all_census_tract_intrinsic.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```



# Model with average $\rho$

```{r}

load(here("modeling_files/all_census_tract_ave_rho.RData"))

```

```{r}
chain1$modelfit

effectiveSize(chain1$samples$beta)

effectiveSize(chain1$samples$sigma2)

effectiveSize(chain1$samples$nu2)
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- c("Intercept", names(fhs_model_df[, 14:(ncol(fhs_model_df) - 1)]))

(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```
