---
title: "Flood Risk PC Coeff Results"
author: "Alvin Sheng"
output: pdf_document
---

```{r}
library(here)
library(tidyverse)
```

For each health outcome, read in the results for the six strata, extract the flood risk PC coefficients, and stack them

# Helper Functions

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inf2data_frame <- function(beta_inference) {
  
  beta_inference_df <- as.data.frame(beta_inference)
  beta_inference_df <- rename(beta_inference_df, 
                              post_median = `50%`,
                              post_2.5 = `2.5%`, 
                              post_97.5 = `97.5%`)
  beta_inference_df$strat <- factor(c(rep("Low SV", (nrow(beta_inference_df)/2)), 
                                         rep("High SV", (nrow(beta_inference_df)/2))), 
                                       levels = c("Low SV", "High SV"))
  
  return(beta_inference_df)
  
}
```

```{r}
# extract the flood risk PC coefficients and stack them
# pc_idx is the vector of indices of the flood risk PC coefficients, after splitting data frame by strata
beta_data_frames_stack <- function(beta_df_list, pc_idx) {
  
  beta_pcs_strat0_list <- list()
  
  beta_pcs_strat1_list <- list()
  
  for (i in 1:length(beta_df_list)) {
    
    beta_inference_df <- beta_df_list[[i]]
    
    beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]
    
    beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
    
    beta_pcs_strat0_list[[i]] <- beta_inference_df_strat0[pc_idx, ]
    
    beta_pcs_strat1_list[[i]] <- beta_inference_df_strat1[pc_idx, ]
    
  }
  
  beta_pcs_strat0 <- do.call("rbind", beta_pcs_strat0_list)
  beta_pcs_strat1 <- do.call("rbind", beta_pcs_strat1_list)
  
  beta_pcs_strat0 <- mutate(beta_pcs_strat0, var_idx = factor(1:nrow(beta_pcs_strat0)))
  beta_pcs_strat1 <- mutate(beta_pcs_strat1, var_idx = factor(1:nrow(beta_pcs_strat1)))
  
  return(list(beta_pcs_strat0 = beta_pcs_strat0, beta_pcs_strat1 = beta_pcs_strat1))
  
}
```





# CHD

```{r}

beta_inf_poverty <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CHD_poverty.rds"))

beta_inf_rpl1 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl1.rds"))

beta_inf_rpl2 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl2.rds"))

beta_inf_rpl3 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl3.rds"))

beta_inf_rpl4 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl4.rds"))

beta_inf_rpls <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpls.rds"))

```



```{r}

beta_inf_poverty_df <- beta_inf2data_frame(beta_inf_poverty)

beta_inf_rpl1_df <- beta_inf2data_frame(beta_inf_rpl1)

beta_inf_rpl2_df <- beta_inf2data_frame(beta_inf_rpl2)

beta_inf_rpl3_df <- beta_inf2data_frame(beta_inf_rpl3)

beta_inf_rpl4_df <- beta_inf2data_frame(beta_inf_rpl4)

beta_inf_rpls_df <- beta_inf2data_frame(beta_inf_rpls)



beta_df_list <- list(beta_inf_poverty_df, beta_inf_rpl1_df, beta_inf_rpl2_df, 
                     beta_inf_rpl3_df, beta_inf_rpl4_df, beta_inf_rpls_df)

```

```{r}
pc_idx <- 2:6
  
beta_CHD_pcs <- beta_data_frames_stack(beta_df_list, pc_idx)
```

```{r}
p <- ggplot(beta_CHD_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.11, 0.065)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = 5 * c(1:5) + 0.5, col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.06, label = "POV\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 8, y = 0.06, label = "Theme 1\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 0.06, label = "Theme 2\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 18, y = 0.06, label = "Theme 3\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23, y = 0.06, label = "Theme 4\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28, y = 0.06, label = "All Theme\nStrata",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = rep(c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6)) + ggtitle("95% Credible Intervals for Flood Risk PCs, Coronary Heart Disease") + 
  geom_point(data = beta_CHD_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_CHD_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}

ggsave(here("figures/final_figures/stratified_analysis_fr_only/CHD_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")

```

Make a summary of significant coefficients and their signs, for each strata

```{r}

signif_summ <- matrix(NA, nrow = 2, ncol = 5 * 6)

row.names(signif_summ) <- c("Low SV", "High SV")
colnames(signif_summ) <- paste(rep(c("POV Strata PC", "Theme 1 Strata PC", "Theme 2 Strata PC", 
                                      "Theme 3 Strata PC", "Theme 4 Strata PC", "All Theme Strata PC"), each = 5),
                                rep(1:5, times = 6))

```

```{r}

for (j in 1:ncol(signif_summ)) {
  
  if(beta_CHD_pcs$beta_pcs_strat0$post_2.5[j] < 0 &
     beta_CHD_pcs$beta_pcs_strat0$post_97.5[j] < 0) {
    signif_summ[1, j] <- "-"
  } else if (beta_CHD_pcs$beta_pcs_strat0$post_2.5[j] > 0 &
     beta_CHD_pcs$beta_pcs_strat0$post_97.5[j] > 0) {
    signif_summ[1, j] <- "+"
  }
  
  if(beta_CHD_pcs$beta_pcs_strat1$post_2.5[j] < 0 &
     beta_CHD_pcs$beta_pcs_strat1$post_97.5[j] < 0) {
    signif_summ[2, j] <- "-"
  } else if (beta_CHD_pcs$beta_pcs_strat1$post_2.5[j] > 0 &
     beta_CHD_pcs$beta_pcs_strat1$post_97.5[j] > 0) {
    signif_summ[2, j] <- "+"
  }
  
}

```

```{r}
t(signif_summ)
```



# BPHIGH

```{r}

beta_inf_poverty <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_poverty.rds"))

beta_inf_rpl1 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl1.rds"))

beta_inf_rpl2 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl2.rds"))

beta_inf_rpl3 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl3.rds"))

beta_inf_rpl4 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl4.rds"))

beta_inf_rpls <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpls.rds"))

```



```{r}

beta_inf_poverty_df <- beta_inf2data_frame(beta_inf_poverty)

beta_inf_rpl1_df <- beta_inf2data_frame(beta_inf_rpl1)

beta_inf_rpl2_df <- beta_inf2data_frame(beta_inf_rpl2)

beta_inf_rpl3_df <- beta_inf2data_frame(beta_inf_rpl3)

beta_inf_rpl4_df <- beta_inf2data_frame(beta_inf_rpl4)

beta_inf_rpls_df <- beta_inf2data_frame(beta_inf_rpls)



beta_df_list <- list(beta_inf_poverty_df, beta_inf_rpl1_df, beta_inf_rpl2_df, 
                     beta_inf_rpl3_df, beta_inf_rpl4_df, beta_inf_rpls_df)

```

```{r}
pc_idx <- 2:6
  
beta_BPHIGH_pcs <- beta_data_frames_stack(beta_df_list, pc_idx)
```

```{r}
p <- ggplot(beta_BPHIGH_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.23, 0.23)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = 5 * c(1:5) + 0.5, col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.22, label = "POV\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 8, y = 0.22, label = "Theme 1\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 0.22, label = "Theme 2\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 18, y = 0.22, label = "Theme 3\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23, y = 0.22, label = "Theme 4\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28, y = 0.22, label = "All Theme\nStrata",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = rep(c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6)) + ggtitle("95% Credible Intervals for Flood Risk PCs, High Blood Pressure") + 
  geom_point(data = beta_BPHIGH_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_BPHIGH_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis_fr_only/BPHIGH_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

Make a summary of significant coefficients and their signs, for each strata

```{r}

signif_summ <- matrix(NA, nrow = 2, ncol = 5 * 6)

row.names(signif_summ) <- c("Low SV", "High SV")
colnames(signif_summ) <- paste(rep(c("POV Strata PC", "Theme 1 Strata PC", "Theme 2 Strata PC", 
                                      "Theme 3 Strata PC", "Theme 4 Strata PC", "All Theme Strata PC"), each = 5),
                                rep(1:5, times = 6))

```

```{r}

for (j in 1:ncol(signif_summ)) {
  
  if(beta_BPHIGH_pcs$beta_pcs_strat0$post_2.5[j] < 0 &
     beta_BPHIGH_pcs$beta_pcs_strat0$post_97.5[j] < 0) {
    signif_summ[1, j] <- "-"
  } else if (beta_BPHIGH_pcs$beta_pcs_strat0$post_2.5[j] > 0 &
     beta_BPHIGH_pcs$beta_pcs_strat0$post_97.5[j] > 0) {
    signif_summ[1, j] <- "+"
  }
  
  if(beta_BPHIGH_pcs$beta_pcs_strat1$post_2.5[j] < 0 &
     beta_BPHIGH_pcs$beta_pcs_strat1$post_97.5[j] < 0) {
    signif_summ[2, j] <- "-"
  } else if (beta_BPHIGH_pcs$beta_pcs_strat1$post_2.5[j] > 0 &
     beta_BPHIGH_pcs$beta_pcs_strat1$post_97.5[j] > 0) {
    signif_summ[2, j] <- "+"
  }
  
}

```

```{r}
t(signif_summ)
```





# CASTHMA

```{r}

beta_inf_poverty <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_poverty.rds"))

beta_inf_rpl1 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl1.rds"))

beta_inf_rpl2 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl2.rds"))

beta_inf_rpl3 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl3.rds"))

beta_inf_rpl4 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl4.rds"))

beta_inf_rpls <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpls.rds"))

```



```{r}

beta_inf_poverty_df <- beta_inf2data_frame(beta_inf_poverty)

beta_inf_rpl1_df <- beta_inf2data_frame(beta_inf_rpl1)

beta_inf_rpl2_df <- beta_inf2data_frame(beta_inf_rpl2)

beta_inf_rpl3_df <- beta_inf2data_frame(beta_inf_rpl3)

beta_inf_rpl4_df <- beta_inf2data_frame(beta_inf_rpl4)

beta_inf_rpls_df <- beta_inf2data_frame(beta_inf_rpls)



beta_df_list <- list(beta_inf_poverty_df, beta_inf_rpl1_df, beta_inf_rpl2_df, 
                     beta_inf_rpl3_df, beta_inf_rpl4_df, beta_inf_rpls_df)

```

```{r}
pc_idx <- 2:6
  
beta_CASTHMA_pcs <- beta_data_frames_stack(beta_df_list, pc_idx)
```

```{r}
p <- ggplot(beta_CASTHMA_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.035, 0.0285)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = 5 * c(1:5) + 0.5, col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.027, label = "POV\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 8, y = 0.027, label = "Theme 1\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 0.027, label = "Theme 2\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 18, y = 0.027, label = "Theme 3\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23, y = 0.027, label = "Theme 4\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28, y = 0.027, label = "All Theme\nStrata",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = rep(c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6)) + ggtitle("95% Credible Intervals for Flood Risk PCs, Asthma") + 
  geom_point(data = beta_CASTHMA_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_CASTHMA_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis_fr_only/CASTHMA_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

Make a summary of significant coefficients and their signs, for each strata

```{r}

signif_summ <- matrix(NA, nrow = 2, ncol = 5 * 6)

row.names(signif_summ) <- c("Low SV", "High SV")
colnames(signif_summ) <- paste(rep(c("POV Strata PC", "Theme 1 Strata PC", "Theme 2 Strata PC", 
                                      "Theme 3 Strata PC", "Theme 4 Strata PC", "All Theme Strata PC"), each = 5),
                                rep(1:5, times = 6))

```

```{r}

for (j in 1:ncol(signif_summ)) {
  
  if(beta_CASTHMA_pcs$beta_pcs_strat0$post_2.5[j] < 0 &
     beta_CASTHMA_pcs$beta_pcs_strat0$post_97.5[j] < 0) {
    signif_summ[1, j] <- "-"
  } else if (beta_CASTHMA_pcs$beta_pcs_strat0$post_2.5[j] > 0 &
     beta_CASTHMA_pcs$beta_pcs_strat0$post_97.5[j] > 0) {
    signif_summ[1, j] <- "+"
  }
  
  if(beta_CASTHMA_pcs$beta_pcs_strat1$post_2.5[j] < 0 &
     beta_CASTHMA_pcs$beta_pcs_strat1$post_97.5[j] < 0) {
    signif_summ[2, j] <- "-"
  } else if (beta_CASTHMA_pcs$beta_pcs_strat1$post_2.5[j] > 0 &
     beta_CASTHMA_pcs$beta_pcs_strat1$post_97.5[j] > 0) {
    signif_summ[2, j] <- "+"
  }
  
}

```

```{r}
t(signif_summ)
```





# MHLTH

```{r}

beta_inf_poverty <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_poverty.rds"))

beta_inf_rpl1 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl1.rds"))

beta_inf_rpl2 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl2.rds"))

beta_inf_rpl3 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl3.rds"))

beta_inf_rpl4 <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl4.rds"))

beta_inf_rpls <- readRDS(here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpls.rds"))

```



```{r}

beta_inf_poverty_df <- beta_inf2data_frame(beta_inf_poverty)

beta_inf_rpl1_df <- beta_inf2data_frame(beta_inf_rpl1)

beta_inf_rpl2_df <- beta_inf2data_frame(beta_inf_rpl2)

beta_inf_rpl3_df <- beta_inf2data_frame(beta_inf_rpl3)

beta_inf_rpl4_df <- beta_inf2data_frame(beta_inf_rpl4)

beta_inf_rpls_df <- beta_inf2data_frame(beta_inf_rpls)



beta_df_list <- list(beta_inf_poverty_df, beta_inf_rpl1_df, beta_inf_rpl2_df, 
                     beta_inf_rpl3_df, beta_inf_rpl4_df, beta_inf_rpls_df)

```

```{r}
pc_idx <- 2:6
  
beta_MHLTH_pcs <- beta_data_frames_stack(beta_df_list, pc_idx)
```

```{r}
p <- ggplot(beta_MHLTH_pcs$beta_pcs_strat0, aes(x = var_idx, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-0.035, 0.05)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = 5 * c(1:5) + 0.5, col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.048, label = "POV\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 8, y = 0.048, label = "Theme 1\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 0.048, label = "Theme 2\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 18, y = 0.048, label = "Theme 3\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23, y = 0.048, label = "Theme 4\nStrata",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28, y = 0.048, label = "All Theme\nStrata",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = rep(c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5"), 6)) + ggtitle("95% Credible Intervals for Flood Risk PCs, Poor Mental Health") + 
  geom_point(data = beta_MHLTH_pcs$beta_pcs_strat1, col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_MHLTH_pcs$beta_pcs_strat1, aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis_fr_only/MHLTH_fr_only.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```

Make a summary of significant coefficients and their signs, for each strata

```{r}

signif_summ <- matrix(NA, nrow = 2, ncol = 5 * 6)

row.names(signif_summ) <- c("Low SV", "High SV")
colnames(signif_summ) <- paste(rep(c("POV Strata PC", "Theme 1 Strata PC", "Theme 2 Strata PC", 
                                      "Theme 3 Strata PC", "Theme 4 Strata PC", "All Theme Strata PC"), each = 5),
                                rep(1:5, times = 6))

```

```{r}

for (j in 1:ncol(signif_summ)) {
  
  if(beta_MHLTH_pcs$beta_pcs_strat0$post_2.5[j] < 0 &
     beta_MHLTH_pcs$beta_pcs_strat0$post_97.5[j] < 0) {
    signif_summ[1, j] <- "-"
  } else if (beta_MHLTH_pcs$beta_pcs_strat0$post_2.5[j] > 0 &
     beta_MHLTH_pcs$beta_pcs_strat0$post_97.5[j] > 0) {
    signif_summ[1, j] <- "+"
  }
  
  if(beta_MHLTH_pcs$beta_pcs_strat1$post_2.5[j] < 0 &
     beta_MHLTH_pcs$beta_pcs_strat1$post_97.5[j] < 0) {
    signif_summ[2, j] <- "-"
  } else if (beta_MHLTH_pcs$beta_pcs_strat1$post_2.5[j] > 0 &
     beta_MHLTH_pcs$beta_pcs_strat1$post_97.5[j] > 0) {
    signif_summ[2, j] <- "+"
  }
  
}

```

```{r}
t(signif_summ)
```


