---
title: "Imported Data Exploration--Census Tract-Level"
author: "Alvin Sheng"
date: "6/8/2021"
output: pdf_document
---

```{r}
library(here)
library(usmap)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
```

```{r}
i_am("reports/imported_data_exploration.Rmd")

select <- dplyr::select
```



# Exploration of Flood Risk Dataset

```{r}
flood_risk <- read.csv(here("imported_data", "flood_risk", "Zip_level_risk_FEMA_FSF_v1.3.csv"))
```

```{r}
summary(flood_risk)
```

There are some missing values in the flood risk. These columns have missing values: 20, 21, 22, 23, and 24. Below shows how many missing values are in each column.

```{r}
missing_idx <- which(is.na(flood_risk), arr.ind = TRUE)

table(missing_idx[, 2])
```

Missing variables are all the "avg_risk_" variables except for "avg_risk_score_all".

```{r}
names(flood_risk)[20:24]
```



# Exploration of the PLACES data set

This data set contains multiple outcomes of interest, as well as multiple covariates of interest. It's currently in long format; it will be turned into wide format. 

```{r}
places_dat <- read.csv(here("imported_data", 
                          "PLACES__Local_Data_for_Better_Health__Census_Tract_Data_2020_release.csv"))
```

```{r}
head(places_dat)
```

Data_Value contains the outcome/covariate values. 

There is only one missing value. 

```{r}
summary(places_dat)
```

There are 28 measures in the data set.

```{r}
unique(places_dat$Measure)
```



The data source for all measures is the Behavioral Risk Factor Surveillance System.

```{r}
table(places_dat$DataSource)
```

3 kinds of outcomes.

```{r}
table(places_dat$Category)
```

All measures are in the form of crude prevalence (%).

```{r}
table(places_dat$Data_Value_Type)
```

MeasureId is a shorter indicator for each of the 28 measures

```{r}
table(places_dat$MeasureId)
```

The data has 72337 out of 73057 census tracts in the U.S. But census tracts can split and merge over time, so the data may actually have all census tracts at that moment in time. 

```{r}
n_distinct(places_dat$LocationName)
```

All but 2 of the census tracts in the PLACES data set are in the CDC SVI data set. Census tracts 6037930401, 15009000320 are not in the CDC SVI data set. 

```{r}
length(intersect(unique(places_dat$LocationID), cdc_svi$fips))
```

LocationName refers to the census tract FIPS. Below is the frequency table of the number of measures associated with a census tract. 99.66 % of census tracts have all 28 measures. 

```{r}
table(as.numeric(table(places_dat$LocationName)))
```



# Exploration of CDC SVI data

```{r}
# reading in the CDC SVI data
cdc_svi <- read.csv(here("imported_data", "CDC_SVI", "SVI2018_US.csv"))

```

```{r}
summary(cdc_svi)
```



# Exploration of CACES LUR air pollution data

```{r}
caces_lur_wide <- readRDS(here("intermediary_data/caces_lur_wide_census_tract.rds"))
```

There is information for 72043 census tracts in the modeling dataset.

```{r}
n_distinct(caces_lur_wide$fips)
```

```{r}
summary(caces_lur_wide)
```



<!-- # Joint exploration of data -->

<!-- The flood risk data doesn't have all the counties. -->

<!-- Exploring the merged dataset -->

<!-- ```{r} -->
<!-- flood_le_svi <- readRDS(file = here("intermediary_data/flood_le_svi.rds")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- dim(flood_le_svi) -->
<!-- ``` -->

<!-- Exploring the modeling dataset -->

<!-- ```{r} -->
<!-- fls_model_df <- readRDS(here("intermediary_data/fls_model_df.rds")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # extract the response variable -->

<!-- Y <- fls_model_df$`Life expectancy, 2014*` -->

<!-- # extract the covariates matrix -->

<!-- X <- fls_model_df[, 17:(ncol(fls_model_df) - 1)] -->

<!-- X <- as.matrix(X) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(Y) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(X) -->
<!-- ``` -->



# Maps

```{r}
library(choroplethr)
```

Census Tracts

```{r}
# plot_usmap(regions = "counties") + 
#   labs(title = "US Counties",
#        subtitle = "This is a blank map of the counties of the United States.") + 
#   theme(panel.background = element_rect(color = "black", fill = "lightblue"))
```



## North Carolina, specifically

```{r}
get_tract_map("north carolina")
```

### Outcome

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_NC_census_tract.rds"))
```

```{r}
outcome_df <- data.frame(region = fhs_model_df$fips, value = fhs_model_df$Data_Value_CHD)
```

```{r}
tract_choropleth(outcome_df, state_name = "north carolina")
```

This function helpfully points out the missing census tract fips in the data set: 

The following regions were missing and are being set to NA: 37031980100, 37141990100, 37119980300, 37133990100, 37095990100, 37129990100, 37019990100, 37173980200, 37053990100, 37031990100, 37093980100, 37087980100, 37183980100, 37055990200, 37183980200, 37063980100, 37119980200, 37129980100, 37051980100, 37055990100, 37119980100, 37089980100, 37081980100.



### Flood Risk Variables

```{r}
fl_df <- data.frame(region = fhs_model_df$fips, value = fhs_model_df$avg_risk_score_all)
```

```{r}
tract_choropleth(fl_df, state_name = "north carolina")
```



### CDC SVI

```{r}
svi_df <- data.frame(region = fhs_model_df$fips, value = fhs_model_df$EP_POV)
```

```{r}
tract_choropleth(svi_df, state_name = "north carolina")
```



### Air Pollution

```{r}
air_df <- data.frame(region = fhs_model_df$fips, value = fhs_model_df$pm25)
```

```{r}
tract_choropleth(air_df, state_name = "north carolina")
```
