---
title: "Imported Data Exploration"
author: "Alvin Sheng"
date: "6/8/2021"
output: pdf_document
---

```{r}
library(here)
library(usmap)
library(ggplot2)
library(tidyverse)
```

```{r}
i_am("reports/imported_data_exploration.Rmd")
```



# Exploration of Flood Risk Dataset

```{r}
flood_risk <- read.csv(here("imported_data", "flood_risk", "County_level_risk_FEMA_FSF_v1.3.csv"))
```

```{r}
summary(flood_risk)
```

There are some missing values in the flood risk.

```{r}
which(is.na(flood_risk), arr.ind = TRUE)
```



# Exploration of Life Expectancy/Mortality Risk data

```{r}
life_expect_mort_no_ui <- readRDS(file = here("imported_data", "life_expectancy_mortality_risk", 
                                              "life_expect_mort_no_ui.rds"))
```

```{r}
summary(life_expect_mort_no_ui)
```



# Exploration of CDC SVI data

```{r}
# reading in the CDC SVI data
cdc_svi <- read.csv(here("imported_data", "CDC_SVI", "SVI2018_US_COUNTY.csv"))

```

```{r}
summary(cdc_svi)
```

# Exploration of Smoking Prevalence Data

<!-- ```{r} -->
<!-- n_distinct(data.frame(smoke_prevalence_both$state, smoke_prevalence_both$county)) -->
<!-- ``` -->

```{r}
smoke_fips <- readRDS(here("intermediary_data/smoke_fips.rds"))
```

```{r}
summary(smoke_fips)
```

The reason there are 11 NAs in the dataset is because I ignored some counties in Alaska and Hawaii, which were merged with other counties in those states. I only "unmerged" the counties within the contiguous U.S. 

```{r}
plot(smoke_fips$total_mean, smoke_fips$daily_mean)
```

The two used variables in the dataset, total_mean and daily_mean, are very correlated (as expected).



# Exploration of CACES LUR air pollution data

```{r}
caces_lur <- read.csv(here("imported_data/caces_lur_air_pollution/caces_lur_air_pollution.csv"))
```

```{r}
# convert from long to wide format

caces_lur_wide <- spread(caces_lur, pollutant, pred_wght)

summary(caces_lur_wide)
```

There is information for all counties in the modeling dataset.

```{r}
n_distinct(caces_lur$fips)
```

```{r}
table(caces_lur$pollutant)
```



# Joint exploration of data

The flood risk data doesn't have all the counties.

Exploring the merged dataset

```{r}
flood_le_svi <- readRDS(file = here("intermediary_data/flood_le_svi.rds"))
```

```{r}
dim(flood_le_svi)
```

Exploring the modeling dataset

```{r}
fls_model_df <- readRDS(here("intermediary_data/fls_model_df.rds"))
```

```{r}
# extract the response variable

Y <- fls_model_df$`Life expectancy, 2014*`

# extract the covariates matrix

X <- fls_model_df[, 17:(ncol(fls_model_df) - 1)]

X <- as.matrix(X)
```

```{r}
summary(Y)
```

```{r}
summary(X)
```

<!-- ```{r} -->
<!-- # omit rows with missing covariate values -->
<!-- Y <- Y[complete.cases(X)] -->
<!-- X <- X[complete.cases(X), ] -->
<!-- # otherwise, S.CARleroux returns "Error: the covariate matrix contains missing 'NA' values." -->

<!-- X <- scale(X) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(X) -->
<!-- ``` -->



# Maps

```{r}
plot_usmap(regions = "counties") + 
  labs(title = "US Counties",
       subtitle = "This is a blank map of the counties of the United States.") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))
```

## Outcome Variables

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "Life expectancy, 2014*", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(name = "Life expectancy (2014)", label = scales::comma) + 
  theme(legend.position = "right")
# labs(title = "US Counties",
#      subtitle = "This is a blank map of the counties of the United States.") + 
# theme(panel.background = element_rect(color = "black", fill = "lightblue"))
```

## Flood Risk Variables

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "avg_risk_score_all", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(name = "Average Risk Score", label = scales::comma,
                        limits = c(0, 10), 
                        breaks = seq(0, 10, 1)) + 
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "avg_risk_fsf_2020_100", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(name = "Average Risk Score, 2020 100-yr", label = scales::comma, 
                        limits = c(0, 10), 
                        breaks = seq(0, 10, 1)) +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "avg_risk_fsf_2020_500", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(name = "Average Risk Score, 2020 500-yr", label = scales::comma, 
                        limits = c(0, 10), 
                        breaks = seq(0, 10, 1)) + 
  theme(legend.position = "right")
```



### Percent of First Street Properties at 3 levels of severity and 2 time points

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "pct_fs_risk_2020_5", color = NA, 
           exclude = c("AK", "HI")) + 
  theme(legend.position = "right") + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100), 
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "Percent 2020, 5-yr")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "pct_fs_risk_2050_5", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100), 
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "Percent 2050, 5-yr") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "pct_fs_risk_2020_100", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100), 
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "Percent 2020, 100-yr") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "pct_fs_risk_2050_100", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100), 
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "Percent 2050, 100-yr") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "pct_fs_risk_2020_500", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100), 
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "Percent 2020, 500-yr") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "pct_fs_risk_2050_500", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100), 
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "Percent 2050, 500-yr") +
  theme(legend.position = "right")
```

### Count of Properties with a given Flood Factor

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "count_floodfactor1", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        # limits = c(0, 100), 
                        # breaks = seq(0, 100, 10),
                        # guide_colourbar(nbin = 100),
                        name = "Flood Factor 1 Count") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "count_floodfactor5", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        # limits = c(0, 100), 
                        # breaks = seq(0, 100, 10),
                        # guide_colourbar(nbin = 100),
                        name = "Flood Factor 5 Count") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "count_floodfactor10", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        # limits = c(0, 100), 
                        # breaks = seq(0, 100, 10),
                        # guide_colourbar(nbin = 100),
                        name = "Flood Factor 10 Count") +
  theme(legend.position = "right")
```



## CDC SVI

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EP_POV", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100),
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "% Poverty") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EPL_POV", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 1),
                        breaks = seq(0, 1, .10),
                        guide_colourbar(nbin = 100),
                        name = "Percentile Poverty") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EP_DISABL", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100),
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "% Disability") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EPL_DISABL", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 1),
                        breaks = seq(0, 1, .10),
                        guide_colourbar(nbin = 100),
                        name = "Percentile Disability") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EP_MINRTY", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100),
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "% Minority") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EPL_MINRTY", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 1),
                        breaks = seq(0, 1, .10),
                        guide_colourbar(nbin = 100),
                        name = "Percentile Minority") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EP_NOVEH", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 100),
                        breaks = seq(0, 100, 10),
                        guide_colourbar(nbin = 100),
                        name = "% No Vehicles") +
  theme(legend.position = "right")
```

```{r}
plot_usmap(regions = "counties", data = flood_le_svi,
           values = "EPL_NOVEH", color = NA, 
           exclude = c("AK", "HI")) + 
  scale_fill_continuous(type = "viridis",
                        limits = c(0, 1),
                        breaks = seq(0, 1, .10),
                        guide_colourbar(nbin = 100),
                        name = "Percentile No Vehicles") +
  theme(legend.position = "right")
```


