---
title: "Mitigation of Multicollinearity Analysis"
author: "Alvin Sheng"
date: '2022-07-24'
output: pdf_document
---

```{r}
library(here)
library(GGally)
library(usdm)
library(factoextra)
library(tidyverse)
```



# Checking for multicollinearity among the covariates

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_all_census_tract_reorg_prev.rds"))
```

## All climate-related variables: flood risk, pollution, and GRIDMET variables

Excluding variables in collin_var_names

```{r}
fr_index <- 19:40

climate_var_idx <- c(fr_index, 57:66)
```

```{r}
ggcorr(data = fhs_model_df[, c(climate_var_idx, ncol(fhs_model_df) - 3)])
```



## Flood risk variables

```{r}
fr_index <- 19:40
```

Variances of the flood risk variables

```{r}
apply(fhs_model_df[fr_index], 2, function(vec) var(vec, na.rm = T))
```

```{r}
ggcorr(data = fhs_model_df[, c(fr_index, ncol(fhs_model_df) - 3)])
```

For each variable, I take the summary of its correlations with other variables, not including itself. 

```{r}
flood_cor <- cor(fhs_model_df[complete.cases(fhs_model_df[, c(fr_index, ncol(fhs_model_df))]), c(fr_index, ncol(fhs_model_df))])

diag(flood_cor) <- NA

summary(flood_cor)
```

Many of the flood risk variables are very correlated.



### PCA with Centering AND Scaling

I think scaling all covariates twice, before and after PCA, will lead to more interpretable results

Conduct PCA on the correlated flood risk variables

```{r}
first_var <- 19

fr_index <- first_var:(first_var + 21)

flood_risk <- fhs_model_df[, fr_index]
```

```{r}
fr_pca <- prcomp(flood_risk[complete.cases(flood_risk),], center = T, scale. = T)

fr_loadings <- fr_pca$rotation
```

```{r}
fviz_eig(fr_pca)
```

```{r}
summ_pca <- summary(fr_pca)

summ_pca$importance[,1:10]
```

We started out with 22 variables. Including five PC scores would include >80% of the variance. 

```{r}
num_pc <- unname(which(summ_pca$importance[3, ] > 0.80)[1])
```

Printing out the loadings, from most negative to least

```{r}
round(fr_loadings[, 1:num_pc], digits = 2)
```

```{r}
# Extract loadings of the variables
fr_loadings_df <- data.frame(Variables = rownames(fr_pca$rotation), fr_pca$rotation)

    # Plot
ggplot(fr_loadings_df) +
  geom_segment(data = fr_loadings_df, aes(x = 0, y = 0, xend = PC1,
     yend = PC2), arrow = arrow(length = unit(1/2, "picas")),
     color = "black") +
  annotate("text", x = (fr_loadings_df$PC1), y = (fr_loadings_df$PC2),
     label = fr_loadings_df$Variables)
```

**Data pre-processing decision: Use first 5 flood risk PCs.**

### Getting the loadings that account for scaling after the PCA

```{r}
pc_sdev <- fr_pca$sdev[1:num_pc]
```

```{r}
fr_loadings_scaled <- sweep(fr_loadings[, 1:num_pc], 2, pc_sdev, FUN = "/")
```

```{r}
round(fr_loadings_scaled, 2)
```

<!-- TODO: flip PC 1, PC 3, PC 4, PC 5 to make them more intuitive -->

```{r}
pc2flip <- c(-1, 1, -1, -1, -1)

fr_loadings_scaled_flipped <- sweep(fr_loadings_scaled, 2, pc2flip, FUN = "*")
```


```{r}
round(fr_loadings_scaled_flipped, 2)
```



## Pollution Variables

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_all_census_tract_reorg_prev.rds"))
```

```{r}
pollute_index <- 57:62

pollute_var <- fhs_model_df[, pollute_index]
```

```{r}
ggcorr(data = pollute_var)
```

```{r}
cor(pollute_var[complete.cases(pollute_var),])
```



### PCA

```{r}
pollute_index <- 57:62

pollute_var <- fhs_model_df[, pollute_index]
```

```{r}
var(pollute_var, na.rm = T)
```

```{r}
pollute_pca <- prcomp(pollute_var[complete.cases(pollute_var),], center = T, scale. = T)

pollute_loadings <- pollute_pca$rotation
```

```{r}
fviz_eig(pollute_pca)
```

First 3 PCs should be sufficient.

```{r}
summ_pca <- summary(pollute_pca)

summ_pca$importance
```

```{r}
round(pollute_loadings, digits = 2)
```


```{r}
# Extract loadings of the variables
pollute_loadings_df <- data.frame(Variables = rownames(pollute_pca$rotation), pollute_pca$rotation)

    # Plot
ggplot(pollute_loadings_df) +
  geom_segment(data = pollute_loadings_df, aes(x = 0, y = 0, xend = PC1,
     yend = PC2), arrow = arrow(length = unit(1/2, "picas")),
     color = "black") +
  annotate("text", x = (pollute_loadings_df$PC1), y = (pollute_loadings_df$PC2),
     label = pollute_loadings_df$Variables)
```

**Data pre-processing decision: Use first 3 pollution PCs.**



## Meteorological Variables

```{r}
mean_df_GRIDMET <- readRDS(file = here("intermediary_data/mean_df_GRIDMET.rds"))

mean_df_GRIDMET$fips <- as.numeric(mean_df_GRIDMET$fips)

mean_df_GRIDMET <- mean_df_GRIDMET[!(mean_df_GRIDMET$fips %in% c(6075980401, 12087980100)), ]
```

```{r}
all.equal(fhs_model_df$fips, mean_df_GRIDMET$fips)
```

```{r}
met_index <- 63:66

met_var <- fhs_model_df[, met_index]
```

```{r}
all_met_var <- cbind(met_var, mean_df_GRIDMET[, -1])

ggcorr(data = all_met_var)
```

```{r}
cor(all_met_var[complete.cases(all_met_var),])
```

### PCA

```{r}
met_index <- 63:66

met_var <- fhs_model_df[, met_index]
```

```{r}
var(met_var[complete.cases(met_var),])
```

```{r}
cor(met_var[complete.cases(met_var),])
```

```{r}
met_pca <- prcomp(met_var[complete.cases(met_var),], center = T, scale. = T)

met_loadings <- met_pca$rotation
```

```{r}
fviz_eig(met_pca)
```

```{r}
summ_pca <- summary(met_pca)

summ_pca$importance
```

```{r}
round(met_loadings, digits = 2)
```


```{r}
# Extract loadings of the variables
met_loadings_df <- data.frame(Variables = rownames(met_pca$rotation), met_pca$rotation)

    # Plot
ggplot(met_loadings_df) +
  geom_segment(data = met_loadings_df, aes(x = 0, y = 0, xend = PC1,
     yend = PC2), arrow = arrow(length = unit(1/2, "picas")),
     color = "black") +
  annotate("text", x = (met_loadings_df$PC1), y = (met_loadings_df$PC2),
     label = met_loadings_df$Variables)
```

**Data pre-processing decision: Use combined tmmx and rmax variables instead of splitting into summer and winter.**



# New data frame (all the new things you did)

Summary of data pre-processing decisions to reduce multicollinearity: 

* Use first 5 flood risk PCs, scaling before and after PCA.
* Use first 3 pollution PCs, scaling before and after PCA.
* Use combined tmmx and rmax variables instead of splitting into summer and winter.

Below is the new set of covariates to be put in the model:

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_fr_and_pollute_pc.rds"))

names(fhs_model_df)[19:(ncol(fhs_model_df) - 4)]
```

## VIF

Let's see if the data pre-processing has improved multicollinearity. With less multicollinearity, the beta estimates will have smaller standard errors. 

```{r}
X <- fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]

X           <- scale(X) # Scale covariates

X <- data.frame(X)
```

```{r}
vif(X)
```

```{r}
vifstep(X)
```

\texttt{vifstep} wasn't able to detect multicollinearity issues. The VIF caps out at 6 for Data_Value_CSmoking. All the climate-related variables and principal components have VIFs that caps out at 2.4. 



# Non-spatial modeling (Preview of results prior to Bayesian CAR modeling)

```{r}
Y <- fhs_model_df$Data_Value_CHD

X <- fhs_model_df[, 19:(ncol(fhs_model_df) - 4)]



X           <- scale(X) # Scale covariates
X[is.na(X)] <- 0        # Fill in missing values with the mean
```

```{r}
fhs_lm <- lm(Y ~ X)
```

```{r}
summary(fhs_lm)
```


