---
title: "Stratified Analysis"
author: "Alvin Sheng"
output: pdf_document
---

```{r}
library(here)
library(coda)
library(CARBayes)
library(ggplot2)
library(tidyverse)
```

```{r}
fhs_model_df <- readRDS("intermediary_data/fhs_model_df_all_census_tract_pc.rds")
```

# Non-Spatial Modeling

```{r}

```



# CAR model results, Coronary Heart Disease Stratified on Poverty

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/model_stratif_poverty.RData"))
```

### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F, include = F}
plot(beta_samples)
```

```{r, eval = F, include = F}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r}
effectiveSize(sigma2_samples)
effectiveSize(nu2_samples)
```

```{r, eval = F, include = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r, eval = F, include = F}
gelman.diag(sigma2_samples)
```

```{r, eval = F, include = F}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r}
effectiveSize(phi_samples_subset)
```

```{r, eval = F, include = F}
plot(phi_samples_subset)
```

```{r, eval = F, include = F}
gelman.diag(phi_samples_subset)
```



## Inference

<!-- TODO: intercept was included by accident. But it'll be ignored in the following results anyway -->

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

# TODO: change to var_names later
colnames(beta_samples_matrix) <- c("strat0",                    
"strat0:flood_risk_pc1",     
"strat0:flood_risk_pc2",     
"strat0:flood_risk_pc3",     
"strat0:flood_risk_pc4",     
"strat0:flood_risk_pc5",     
"strat0:EP_UNEMP",           
"strat0:EP_PCI",             
"strat0:EP_NOHSDP",          
"strat0:EP_AGE65",           
"strat0:EP_AGE17",           
"strat0:EP_DISABL",          
"strat0:EP_SNGPNT",          
"strat0:EP_MINRTY",          
"strat0:EP_LIMENG",          
"strat0:EP_MUNIT",          
"strat0:EP_MOBILE",          
"strat0:EP_CROWD",           
"strat0:EP_NOVEH",           
"strat0:EP_GROUPQ",          
"strat0:EP_UNINSUR",         
"strat0:co",                 
"strat0:no2",                
"strat0:o3",                 
"strat0:pm10",               
"strat0:pm25",               
"strat0:so2",                
"strat0:summer_tmmx",        
"strat0:winter_tmmx",        
"strat0:summer_rmax",        
"strat0:winter_rmax",        
"strat0:Data_Value_CSMOKING",
"strat1",                    
"strat1:flood_risk_pc1",     
"strat1:flood_risk_pc2",     
"strat1:flood_risk_pc3",     
"strat1:flood_risk_pc4",     
"strat1:flood_risk_pc5",     
"strat1:EP_UNEMP",           
"strat1:EP_PCI",             
"strat1:EP_NOHSDP",          
"strat1:EP_AGE65",           
"strat1:EP_AGE17",           
"strat1:EP_DISABL",          
"strat1:EP_SNGPNT",          
"strat1:EP_MINRTY",          
"strat1:EP_LIMENG",          
"strat1:EP_MUNIT",           
"strat1:EP_MOBILE",          
"strat1:EP_CROWD",           
"strat1:EP_NOVEH",           
"strat1:EP_GROUPQ",          
"strat1:EP_UNINSUR",         
"strat1:co",                 
"strat1:no2",                
"strat1:o3",                 
"strat1:pm10",               
"strat1:pm25",               
"strat1:so2",                
"strat1:summer_tmmx",        
"strat1:winter_tmmx",        
"strat1:summer_rmax",       
"strat1:winter_rmax",        
"strat1:Data_Value_CSMOKING") # var_names
```

```{r}
(beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5))
```

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- factor(beta_inference_df$var_name, levels = beta_inference_df$var_name)
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata (corresponding to poverty) is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 10)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(5.5, 20.5, 26.5, 30.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3.5, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23.5, y = 1.5, label = "Air Pollution",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28.5, y = 1.5, label = "GRIDMET",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5",
                              "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "CO", "NO2", "O3", "PM10", "PM2.5", "SO2",
                              "Summer Temperature", "Winter Temperature", "Summer Humidity", "Winter Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Lower Strata")

p
```

```{r}
p <- ggplot(beta_inference_df_strat1[-1, ], aes(x = var_name, y = post_median)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 10)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4)) + 
  geom_vline(xintercept = c(5.5, 20.5, 26.5, 30.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3.5, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 23.5, y = 1.5, label = "Air Pollution",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 28.5, y = 1.5, label = "GRIDMET",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("PC 1", "PC 2", "PC 3", "PC 4", "PC 5",
                              "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "CO", "NO2", "O3", "PM10", "PM2.5", "SO2",
                              "Summer Temperature", "Winter Temperature", "Summer Humidity", "Winter Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Upper Strata")

p
```


