---
title: "Stratified Analysis"
author: "Alvin Sheng"
output: 
  pdf_document:
    toc: true
---

\newpage

```{r}
library(here)
library(coda)
library(CARBayes)
library(ggplot2)
library(tidyverse)
```

```{r}
fhs_model_df <- readRDS(here("intermediary_data/fhs_model_df_all_census_tract_pc.rds"))
```

Function for post-processing the inference

```{r}
pc2flip <- c(-1, 1, -1, -1, -1, 
             -1, 1, -1, -1, -1)

post_flip <- function(beta_inf_subset, pc2flip) {
  names_temp <- colnames(beta_inf_subset)
  beta_inf_subset[pc2flip == -1, ] <- beta_inf_subset[pc2flip == -1, c(1, 3, 2)]
  colnames(beta_inf_subset) <- names_temp
  return(sweep(beta_inf_subset, 1, pc2flip, FUN = "*"))
}
```

# Effect Size Analysis

Recall that regression coefficient estimates $\hat{\beta}$ can be standardized in the following manner:
$$\hat{\beta}^* = \frac{SD(X)}{SD(Y)} \hat{\beta},$$
where $SD(X)$ is the standard deviation of the covariate that $\hat{\beta}$ corresponds to, and $SD(Y)$ is the standard deviation of the response variable, i.e., one of the health outcomes. 

In the present analysis, the covariates have been scaled by their standard deviations, but the response variable has not been scaled. Denote the regression coefficient estimates of this analysis as $\hat{b}$, such that

$$\hat{\beta}^* = \frac{\hat{b}}{SD(Y)}$$

Acock (2014, p. 272) suggests the following effect size heuristic for standardized beta coefficients $\hat{\beta}^*$: 

1. Weak: $|\hat{\beta}^*| < 0.2$
2. Moderate: $0.2 < |\hat{\beta}^*| < 0.5$
3. Strong: $|\hat{\beta}^*| > 0.5$

Citation: Acock, A. C. (2014). A Gentle Introduction to Stata (4th ed.). Texas: Stata Press.

Translating the heuristic for our estimates $\hat{b}$, we have that

1. Weak: $|\hat{b}| < 0.2 \times SD(Y)$
2. Moderate: $0.2 \times SD(Y) < |\hat{b}| < 0.5 \times SD(Y)$
3. Strong: $|\hat{b}| > 0.5 \times SD(Y)$

In the following ggplots, I include the positive/negative cut-off for the "Weak" effect size as dashed red lines. 

```{r}
# standard deviations for the health outcome variables

(sd_CHD <- sd(fhs_model_df$Data_Value_CHD, na.rm = T))

(sd_BPHIGH <- sd(fhs_model_df$Data_Value_BPHIGH, na.rm = T))

(sd_CASTHMA <- sd(fhs_model_df$Data_Value_CASTHMA, na.rm = T))

(sd_MHLTH <- sd(fhs_model_df$Data_Value_MHLTH, na.rm = T))

```

# CHD Stratified Analysis

## CAR model results, Coronary Heart Disease Stratified on Poverty

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_poverty.RData"))
```

### Beta samples

```{r}
beta_samples <- mcmc.list(chain1$samples$beta, chain2$samples$beta, 
                          chain3$samples$beta)
```

```{r}
effectiveSize(beta_samples)
```

```{r, eval = F, include = F}
plot(beta_samples)
```

```{r, eval = F, include = F}
gelman.diag(beta_samples)
```




### Examining sigma2, nu2, rho

```{r}
sigma2_samples <- mcmc.list(chain1$samples$sigma2, chain2$samples$sigma2, 
                            chain3$samples$sigma2)

nu2_samples <- mcmc.list(chain1$samples$nu2, chain2$samples$nu2, 
                         chain3$samples$nu2)

```

```{r}
effectiveSize(sigma2_samples)
effectiveSize(nu2_samples)
```

```{r, eval = F, include = F}
plot(sigma2_samples)

plot(nu2_samples)
```

```{r, eval = F, include = F}
gelman.diag(sigma2_samples)
```

```{r, eval = F, include = F}
gelman.diag(nu2_samples)
```



### Examining a sample of the 3108 phi parameters

```{r}
phi_samples <- mcmc.list(chain1$samples$phi, chain2$samples$phi, chain3$samples$phi)
```

```{r}
set.seed(1157, kind = "Mersenne-Twister", normal.kind = "Inversion", sample.kind = "Rejection")

phi_subset_idx <- sample(1:ncol(phi_samples[[1]]), size = 10)

phi_samples_subset <- phi_samples[, phi_subset_idx]
```

```{r}
effectiveSize(phi_samples_subset)
```

```{r, eval = F, include = F}
plot(phi_samples_subset)
```

```{r, eval = F, include = F}
gelman.diag(phi_samples_subset)
```



### Inference

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_poverty.rds"))
```

List of significant beta coefficients: 

```{r}
colnames(beta_samples_matrix)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand

beta_inference_df <- as.data.frame(beta_inference)

beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))

beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)

beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))

beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 20.5, 23.5, 25.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Stratified on Poverty") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_poverty.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



## CAR model results, Coronary Heart Disease Stratified on RPL_THEME1

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl1.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl1.rds"))
```



List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Stratified on RPL Theme 1") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_rpl1.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## CAR model results, Coronary Heart Disease Stratified on RPL_THEME2

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl2.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl2.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Stratified on RPL Theme 2") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_rpl2.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## CAR model results, Coronary Heart Disease Stratified on RPL_THEME3

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl3.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl3.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 19.5, 22.5, 24.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Stratified on RPL Theme 3") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_rpl3.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## CAR model results, Coronary Heart Disease Stratified on RPL_THEME4

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl4.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpl4.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 16.5, 19.5, 21.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11, y = 1.5, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Minority", "Poor English",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Stratified on RPL Theme 4") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_rpl4.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## CAR model results, Coronary Heart Disease Stratified on RPL_THEMES

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpls.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CHD_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 1.45, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Coronary Heart Disease, Stratified on All RPL Themes") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CHD_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



# BPHIGH Stratified Analysis

Repeating the stratified analysis in the last section, this time just doing the plots

## Stratified on Poverty

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_poverty_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_poverty.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 20.5, 23.5, 25.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 4, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, High Blood Pressure, Stratified on Poverty") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_poverty.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



## Stratified on RPL_THEME1

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl1_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl1.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 4, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, High Blood Pressure, Stratified on RPL Theme 1") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_rpl1.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME2

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl2_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl2.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 4, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, High Blood Pressure, Stratified on RPL Theme 2") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_rpl2.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME3

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl3_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl3.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 19.5, 22.5, 24.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 4, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, High Blood Pressure, Stratified on RPL Theme 3") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_rpl3.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME4

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl4_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpl4.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 16.5, 19.5, 21.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11, y = 4, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Minority", "Poor English",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, High Blood Pressure, Stratified on RPL Theme 4") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_rpl4.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEMES

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpls_BPHIGH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/BPHIGH_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-3, 5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, High Blood Pressure, Stratified on All RPL Themes") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/BPHIGH_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





# CASTHMA Stratified Analysis

Repeating the stratified analysis in the last section, this time just doing the plots

## Stratified on Poverty

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_poverty_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_poverty.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 20.5, 23.5, 25.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 1, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on Poverty") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CASTHMA_CI_poverty.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



## Stratified on RPL_THEME1

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl1_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl1.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 1, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on RPL Theme 1") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CASTHMA_CI_rpl1.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME2

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl2_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl2.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 1, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on RPL Theme 2") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CASTHMA_CI_rpl2.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME3

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl3_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl3.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 19.5, 22.5, 24.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 1, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on RPL Theme 3") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CASTHMA_CI_rpl3.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME4

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl4_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpl4.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 16.5, 19.5, 21.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11, y = 1, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Minority", "Poor English",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on RPL Theme 4") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CASTHMA_CI_rpl4.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEMES

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpls_CASTHMA.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/CASTHMA_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1, 1.5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 0.95, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Asthma, Stratified on All RPL Themes") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/CASTHMA_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





# MHLTH Stratified Analysis

Repeating the stratified analysis in the last section, this time just doing the plots

## Stratified on Poverty

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_poverty_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_poverty.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() +
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 20.5, 23.5, 25.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 13, y = 3.8, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Poor Mental Health, Stratified on Poverty") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/MHLTH_CI_poverty.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



## Stratified on RPL_THEME1

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl1_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl1.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 3.8, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent", "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Poor Mental Health, Stratified on RPL Theme 1") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)
p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/MHLTH_CI_rpl1.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME2

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl2_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl2.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 17.5, 20.5, 22.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11.5, y = 3.8, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "Minority", "Poor English",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Poor Mental Health, Stratified on RPL Theme 2") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/MHLTH_CI_rpl2.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME3

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl3_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl3.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 19.5, 22.5, 24.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 12.5, y = 3.8, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Multi-Unit", "Mobile", "Crowded",
                              "No Vehicle", "Group Quarters", "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Poor Mental Health, Stratified on RPL Theme 3") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/MHLTH_CI_rpl3.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEME4

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpl4_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpl4.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 16.5, 19.5, 21.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  annotate(geom = "text", x = 11, y = 3.8, label = "Social Vulnerability Index",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Poverty", "Unemployed", "Per Capita Income", "No High School",
                              "65 or Over", "17 or Under", "Disability",
                              "Single-Parent",
                              "Minority", "Poor English",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Poor Mental Health, Stratified on RPL Theme 4") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/MHLTH_CI_rpl4.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```





## Stratified on RPL_THEMES

Inference is based on 3 markov chains, each of which has been run for 110000 samples, the first 10000 of which has been removed for burn-in. The remaining 100000 samples are thinned by 2, resulting in 150000 samples for inference across the 3 Markov chains. 

```{r}
load(here("modeling_files/stratified_analysis/model_stratif_rpls_MHLTH.RData"))
```

```{r}
beta_samples_matrix <- rbind(chain1$samples$beta, chain2$samples$beta, chain3$samples$beta)

colnames(beta_samples_matrix) <- var_names
```

```{r}
beta_inference <- round(t(apply(beta_samples_matrix, 2, quantile, c(0.5, 0.025, 0.975))),5)

pc_idx <- c(2:6, 
            nrow(beta_inference)/2 + 2:6)

# flipping the inference results according to the flipped PCs
beta_inference[pc_idx, ] <- post_flip(beta_inference[pc_idx, ], pc2flip)

beta_inference
```

```{r}
saveRDS(beta_inference, file = here("modeling_files/stratified_analysis/beta_inference_files/MHLTH_rpls.rds"))
```

List of significant beta coefficients: 

```{r}
row.names(beta_inference)[sign(beta_inference[, 2]) == sign(beta_inference[, 3])]
```



### Credible Interval plots for the coefficients, in ggplot

```{r}
# first, process the beta_inference matrix in a form ggplot can understand
beta_inference_df <- as.data.frame(beta_inference)
beta_inference_df <- mutate(beta_inference_df, var_name = row.names(beta_inference_df))
beta_inference_df <- rename(beta_inference_df, 
                            post_median = `50%`,
                            post_2.5 = `2.5%`, 
                            post_97.5 = `97.5%`)
beta_inference_df$var_name <- substring(beta_inference_df$var_name, first = 8)
beta_inference_df$var_name <- factor(beta_inference_df$var_name, 
                                     levels = unique(beta_inference_df$var_name))
beta_inference_df$strat <- as.factor(c(rep("Lower", (nrow(beta_inference_df)/2)), 
                                       rep("Upper", (nrow(beta_inference_df)/2))))
```

Splitting up the beta coefficients for each strata

```{r}
beta_inference_df_strat0 <- beta_inference_df[1:(nrow(beta_inference_df)/2),]

beta_inference_df_strat1 <- beta_inference_df[(nrow(beta_inference_df)/2 + 1):nrow(beta_inference_df),]
```

Note: The intercept for both strata is not included.

```{r}
p <- ggplot(beta_inference_df_strat0[-1, ], aes(x = var_name, y = post_median, color = strat)) + 
  geom_point() + 
  ylim(c(-1.5, 4)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank(), axis.title.y = element_blank(), 
        axis.text=element_text(size=12), 
        plot.margin = margin(5.5, 5.5, 5.5, 25)) +
  geom_errorbar(aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#F8766D") + 
  geom_vline(xintercept = c(5.5, 6.5, 9.5, 11.5), col = "blue") +
  geom_hline(yintercept = 0, col = "red") +
  annotate(geom = "text", x = 3, y = 3.75, label = "Flood\nRisk",
           col = "blue", size = 4.5) +
  scale_x_discrete(labels = c("Flood PC 1", "Flood PC 2", "Flood PC 3", "Flood PC 4", "Flood PC 5",
                              "Uninsured",
                              "Pollution PC 1", "Pollution PC 2", "Pollution PC 3",
                              "Maximum Temperature", "Maximum Humidity",
                              "Smoking")) + ggtitle("95% Credible Intervals, Poor Mental Health, Stratified on All RPL Themes") + 
  geom_point(data = beta_inference_df_strat1[-1, ], col = "#00BFC4") + # strat 1
  geom_errorbar(data = beta_inference_df_strat1[-1, ], aes(ymin = post_2.5, ymax = post_97.5, width = 0.4), col = "#00BFC4") + 
  scale_color_manual(name = "Strata",
                     values = c("#F8766D", "#00BFC4"), 
                     drop = FALSE)

p
```

```{r}
ggsave(here("figures/final_figures/stratified_analysis/MHLTH_CI_rpls.pdf"),
       plot = p, device = "pdf", 
       width = 8, height = 6, units = "in")
```



